---
title: "Project manuals"
author: "from Daniel Welz, Augustin Oltramare , Marine  "
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
bibliography: references.bib
link-citations: yes
runtime: shiny
---

```{r, echo = FALSE, message = FALSE}
source(here::here("setup.R"))
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Research objective

1)  Does the presence of CCTVs in a given area actually deter crime?

* Goal: Yes-or-no answer.Yes, in neighborhoods x,y,z (if conditions x,y,z are met). No, in neighborhoods x,y,z (if conditions x,y,z not met). What are the differences (critical variables), when CCTS deter crime.  
* Communicate goal: Show map of Baltimore with neighborhoods (graphical respresentation). Either completely red (no deterring of crime), or green (deterring of crime) or yellow (no effect).
* Steps: 
* Needed packages: 
* Things to consider: 


2)  What types of crimes may be deterred by surveillance cameras?

* Goal:Crime reduction by type. 
* Communicate goal: Crime type overview. For each crime show reduction (effect of installation). Summarize on which three crimes it actually has most significant impact. 
* Steps: 
* Needed packages: 
* Things to consider: 


3)  Is the impact of CCTV installation on crime reduction higher/lower/same in higher income neighborhoods compared to lower income
    neighborhoods?
    
* Goal: Comparison impact on neighborhood + Root causes
* Communicate goal: Show top 3 impacted neighborhoods, show top 3 less impacted neighborhoods, explain three reasons why difference (compenents x,y,z)
* Steps: 
* Needed packages: 
* Things to consider: 

4)  Are there more public cameras in lower income/higher unemployment areas compared to higher income/employment areas? (Does the government         respect privacy issues depending on your income level?) 

* Goal:
* Communicate goal: 
* Steps: 
* Needed packages: 
* Things to consider: 


5)  Do we observe crime displacement issues caused by the installation of CCTV in some neighbourhoods?

* Goal:
* Communicate goal: 
* Steps: 
* Needed packages: 
* Things to consider: 

