---
title: "Marine_Cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Research question : n°4 : Are there more public cameras in lower income/higher unemployment areas compared to higher income/employment areas? (Does the government respect privacy issues depending on your income level?).

#Steps : Create clusters with concentration of cctvs in each of the 55 area / Compare to poverty rate in each of the 55 areas.


#Importation des fichiers

getwd()
setwd("/Users/renaudineaumarine/Documents/GitHub/DSBA-Group10/WD")

cctv_data <- read.csv("Baltimore_CCTV_Locations_Crime_Cameras.csv")
area_data <- read.csv("Community_Statistical_Areas__CSAs___Reference_Boundaries.csv")
poverty_data <- read.csv("Percent_of_Family_Households_Living_Below_the_Poverty_Line.csv")

#Affichage des datasets

View(cctv_data)
View(area_data)
View(poverty_data)


#Packages et librairies

library(tidyverse)
library(data.table)
library(sp)
library(rgdal)
library(ggplot2)


#Faire un tableau qui calcule le nombre de cameras selon les districts (fait par Augustin)

#Calculation of the density of CCTV per community

#read in data table
balt_dat <- fread("Baltimore_CCTV_Locations_Crime_Cameras.csv")

#convert to data table
balt_dat <- as.data.table(balt_dat)

#make data spatial
coordinates(balt_dat) <-  c("X","Y")
crs.geo1 <-  CRS("+proj=merc +a=6378137 +b=6378137 +lat_ts=0 +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs +type=crs")
proj4string(balt_dat) <-  crs.geo1  

plot(balt_dat, pch = 20, col = "steelblue")

#read in shapefile of baltimore
baltimore <-  readOGR(dsn = "./Community_Statistical_Area", layer = "Community_Statistical_Area") #name of file and object
proj4string(baltimore) <- crs.geo1

#plot
plot(baltimore,main="Spread of CCTVs in different communities of Baltimore")
plot(balt_dat,pch=20, col="steelblue" , add=TRUE)

#Perform the count

proj4string(balt_dat)
proj4string(baltimore)

res2 <- over(balt_dat,baltimore)
counts <- table(res2$community)
counts <- as.data.frame(counts)
colnames(counts)[1] <- "Community"
sum(counts$Freq)

#Calculate the density for each community 

CCTV_per_area <- area_data[2] %>% 
  left_join(counts,by="Community") #One must add the communities where there are no counts i.e no CCTV

CCTV_per_area[is.na(CCTV_per_area)] <- 0

CCTV_per_area <- mutate(CCTV_per_area, density_perc=(CCTV_per_area$Freq/(sum(CCTV_per_area$Freq)))*100)

View(CCTV_per_area)


#Comparison of CCTV density vs wealth

```{r}

poverty_data <- rbind(poverty_data,list(56,"Unassigned -- Jail",0,0,0,0,0,0,0))

plot(CCTV_per_area$density_perc,poverty_data$hhpov19, main="CCTV density VS poverty rate",xlab="CCTV Density",ylab="Poverty rate")

regression2 <- lm(poverty_data$hhpov19~CCTV_per_area$density_perc)
summary(regression2)

y2<-regression2[["coefficients"]][["(Intercept)"]]
x2<-regression2[["coefficients"]][["CCTV_per_area$density_perc"]]

range2 <- seq(from=-5, to=12, by=0.2)

estimation2 <- x2*range2+y2

lines(range2,estimation2, col="blue")
```


# Créer un tableau comparatif avec : une colonne pour le nom des areas, une colonne pour le nbr de cameras, une colonne pour le taux de 'pauvreté' dans l'area. 



