---
title: "Data Science for Business Analytics: Project draft"
author: "from Daniel Welz, Augustin Oltramare , Marine [Add surname] "
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
bibliography: references.bib
link-citations: yes
runtime: shiny
---

```{r, echo = FALSE, message = FALSE}
source(here::here("setup.R"))
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#---
title: "Data Science - Project Proposal"
author: Marine Renaudineau, Daniel Welz & Augustin Oltramare
date: "17/10/2021"
output: html_document
---

#Test 3

# Background and motivation (Marine, Augustin, Daniel)

(- Privacy matters a lot to us. We see a  tendency of the government and other stakeholder (e.g. businesses such as GAFA) to take more and more control in our daily lives. We think we have a right to privacy. 
- University courses: Digital privacy. GDPR course, law about what government can do or not with our personal data
- Refer to critical articles)

Privacy matters a lot to us. We see a tendency of the government and other stakeholder (e.g. businesses such as GAFA) to take more and more control in our daily lives. We think we have a right to privacy. It is interesting to ask ourselves if this massive collection of our data leads to more security or more restrictions of our freedoms. 

If we look at European laws like the GDPR, the collection and processing of our data must be proportionate to the purpose of that processing. Therefor, It is of interest for us to determine if these applications are the same in the United States and to see if the installation of cameras, with the objective of security, really allows to reduce crime and to secure a city. 

It must also be said that crime in the United-States is fascinating. The freedom to carry a gun gives the impression that US is more prone to crimes such as mass shootings. We also want to see through this dataset what kind of crime prevails in an American city and how it evolves according to the districts and their particularities.  

We also find that studying this dataset on security camera placement is a good approach to answer these questions. 

Here are some good articles that guided us in our research : 
https://www.activemind.legal/guides/cctv-data-protection/
https://edps.europa.eu/data-protection/data-protection/reference-library/video-surveillance_en 


# Project objectives (Augustin and Daniel)

Video surveillance (CCTV) is a technology that is nowadays deeply woven into the everyday life of many people as one tends to expect it in many varied circumstances (Ossola, 2019). The rationale behind the installation of these systems seems to be very clear for governments. On Buffalo’s (NY) open data website, one can read that “the City of Buffalo deploys a real-time, citywide video surveillance system to augment the public safety efforts of the Buffalo Police Department”. Yet, the development of this new technology, is not exempt from any controversy. For instance, many observers claim that the expansion of video surveillance poses an unregulated threat to privacy (ACLU, 2021). Still, many people seem to be willing to accept this loss in privacy as the surge in video surveillance makes them feel safer (Madden & Rainie, 2015).

Throughout this research, the widespread belief that people who have “nothing to hide" should be content with the expansion of CCTV networks as the latter make them safer is therefore challenged (Madden & Rainie, 2015). Indeed, on top of the manifold privacy issues linked with this surge in video surveillance systems, one might legitimately ask the question whether these cameras actually make people safer?

The goal of this project is to first investigate the crime deterrent potential of CCTVs in a US city. This potential will also be compared to the different types of crime that are committed in this area. Over a second phase, the dispersion of CCTVs within the city will be investigated. Indeed, according to some researches, mass surveillance has a stronger impact on communities already disadvantaged by their poverty, race, religion, ethnicity, or immigration status (Gellman & Adler-Bell, 2017). We would like to see whether our data enables us to validate or invalidate this theory. It would also be extremely interesting, even though tricky, to see whether the installation of surveillance systems could potentially create even more pernicious issues such as crime displacement.

In a world where CCTVs and other surveillance systems are flourishing, it might be beneficial to take a step back and question both the efficacy and the implementation design of such technologies often portrayed as miraculous solutions.

# Research questions 

- Does the presence of CCTVs in a given area actually deter crime?
- What types of crimes may be deterred by surveillance cameras?
- Is the impact of CCTV installation on crime reduction higher/lower/same in higher income neighborhoods compared to lower income neighborhoods?
- Are there more public cameras in lower income/higher unemployment areas compared to higher income areas? (Does the government respect privacy issues depending on your income level?) 
- Do we observe crime displacement issues caused by the installation of CCTV in some neighbourhoods?

# Data source (Augustin, Daniel, Marine)

All data sets were retrieved on local government open data portals (https://data.baltimorecity.gov / https://data.buffalony.gov / https://opendata.dc.gov). We initially found data sets regarding 3 different cities in the United States: Baltimore (MD), Buffalo (NY) and Washington (DC). For each city we found data sets on crimes committed in these respective areas, CCTV locations and neighbourhood metrics. We quickly realised that, for feasibility reasons, we should focus on one city only. As the neighbourhood metrics we found about Washington seemed less complete, we quickly ruled out this option. Using a KML file visualizer to compare the CCTV locations of Buffalo and Baltimore, we found out that the CCTV data set for Baltimore was more complete. Furthermore, by simply looking at the map we found some seemingly intriguing patterns (cf: two screenshots attached). Thus, we finally decided to opt for Baltimore. On Baltimore open data portal, we finally found a data set showing the reference boundaries of the Community Statistical Area geographies. The latter will certainly be helpful to match each data set's observations togehther.

# Data description (Daniel, Augustin, Marine)

Data set about criminality in  Baltimore: This dataset represents the location and characteristics of major (Part 1) crime against persons such as homicide, shooting, robbery, aggrevated assault etc. within the City of Baltimore. Data updated as of October 05, 2021 at 13:56:39. 

Data set about CCTV location in Baltimore: This dataset represents closed circuit camera locations capturing activity within 256ft (~2 blocks).

Data set about neighbourhood metrics: This dataset provides information about the percent of Family Households Living Below the Poverty Line. This indicator measures the percentage of households whose income fell below the poverty threshold out of all households in an area. Federal and state governments use such estimates to allocate funds to local communities. Local communities use these estimates to identify the number of individuals or families eligible for various programs. This dataset contains 55 observation, one percentage for each community statistical area. The most relevant variables are the following: 

CSA2010 = name of the community statistical area. The Baltimore Data Collaborative and the Baltimore City Department of Planning divided Baltimore into 55 CSAs. These 55 units combine Census Bureau geographies together in ways that match Baltimore’s understanding of community boundaries, and are used in social planning.

hhpov15 - hhpov19 = each these five column contains the percent of Family Households Living Below the Poverty Line for a given year.

Shape__Area - Shape__Length = 

Data set about Community Statistical Areas: This dataset provides information about the Community Statistical Area geographies for Baltimore City. Based on aggregations of Census tract (2010) geographies.


- Describe columns/variables
- Describe which type of data
- Describe how clean the provided datasets are?


# Schedule & timeline (Done)

We agreed on meeting on a daily basis (every Thurdays at 0130 PM). The milestones of our project are the following:

21/10 - Thursday meeting at 1:30 PM

1) For each research question, write down exactly the steps which need to be made with the data. Step-by-step (Which variables are important to answering the research question: Then we have 5 manuals in the end, which needed to be executed.)
2) Start tidy datasets (Remove N.As) - We have 3 datasets for Baltimore

28/10 - Thursday meeting at 1:30 PM

1) Start tidy datasets (Remove N.As) - We have 3 datasets for Baltimore
2) Fix bugs/ iterate and ask questions
3) TBD

04/11 - Thursday meeting at 1:30 PM

TBD

10/11 - Project update 

TBD

11/11 - Thursday meeting at 1:30 PM

TBD

18/11 - Thursday meeting at 1:30 PM

TBD

25/11 - Thursday meeting at 1:30 PM

TBD

4/12 - Thursday meeting at 1:30 PM

TBD

11/12 - Thursday meeting at 1:30 PM


15/12 - Final report



