---
title: "Data Science for Business Analytics: Project draft"
author: "from Daniel Welz, Augustin [Add surname] , Marine [Add surname] "
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
bibliography: references.bib
link-citations: yes
runtime: shiny
---

```{r, echo = FALSE, message = FALSE}
source(here::here("setup.R"))
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#test

#test2

#Showing R 

#---
title: "Data Science - Project Proposal"
author: Marine Renaudineau, Daniel Welz & Augustin Oltramare
date: "17/10/2021"
output: html_document
---

# Background and motivation

- Privacy matters a lot to us. We see a  tendency of the government and other stakeholder (e.g. businesses such as GAFA) to take more and more control in our daily lives. We think we have a right to privacy. 
- University courses: Digital privacy. GDPR course, law about what government can do or not with our personal data
- Refer to critical articles


# Project objectives

Video surveillance (CCTV) is a technology that is nowadays deeply woven into the everyday life of many people as one tends to expect it in many varied circumstances (Ossola, 2019). Yet, the development of this new technology, is not exempt from any controversy. For instance, many observers claim that the expansion of video surveillance poses an unregulated threat to privacy (ACLU, 2021). Still, many people seem to be willing to accept this loss in privacy as the surge in video surveillance make them feel safer (Madden & Rainie, 2015).

Throughout this research, the widespread belief that people who have “nothing to hide" should be content with the expansion of CCTV networks as the latter makes them safer is challenged (Madden & Rainie, 2015). Indeed, on top of the manifold privacy issues linked with this surge in video surveillance systems, one might ask the question wether these camera actually make people safer?

On the one hand, the rationale behind the installation of these systems seems to be very clear for governments. On Buffalo’s open data website, one can read that “the City of Buffalo deploys a real-time, citywide video surveillance system to augment the public safety efforts of the Buffalo Police Department”. Yet, on the other one, evidence that this actually works is scarcer.


# Research questions

- Does the presence of CCTVs actually deter crime?
- What types of crimes may be deterred by surveillance cameras?
- Do we observe crime displacement issues caused by the installation of CCTV in some neighbourhoods?
- Is the impact of CCTV installment on crime reduction higher/lower/same in higher income neighborhoods compared to lower income neighborhoods?
- Are there more public cameras in lower income/higher unemployment areas compared to higher income areas? (Does the government respect privacy issues dependening on your income level?)

# Data source

All data sets were retrieved on local government open data portals. At the moment, we have 7 data sets. We have data concerning 3 different cities in the United States: Baltimore, Buffalo and Washington DC.

# Data description

- Describe columns
- Describe which type of data
- Describe how clean the provided datasets are? 


# Schedule & timeline

