---
title: "Data Science for Business Analytics: Project draft"
author: "from Daniel Welz, Augustin Oltramare , Marine [Add surname] "
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
bibliography: references.bib
link-citations: yes
runtime: shiny
---

```{r, echo = FALSE, message = FALSE}
source(here::here("setup.R"))
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#---
title: "Data Science - Project Proposal"
author: Marine Renaudineau, Daniel Welz & Augustin Oltramare
date: "17/10/2021"
output: html_document
---

# Background and motivation (Marine, Augustin, Daniel)

- Privacy matters a lot to us. We see a  tendency of the government and other stakeholder (e.g. businesses such as GAFA) to take more and more control in our daily lives. We think we have a right to privacy. 
- University courses: Digital privacy. GDPR course, law about what government can do or not with our personal data
- Refer to critical articles


# Project objectives (Augustin and Daniel)

Video surveillance (CCTV) is a technology that is nowadays deeply woven into the everyday life of many people as one tends to expect it in many varied circumstances (Ossola, 2019). The rationale behind the installation of these systems seems to be very clear for governments. On Buffalo’s (NY) open data website, one can read that “the City of Buffalo deploys a real-time, citywide video surveillance system to augment the public safety efforts of the Buffalo Police Department”. Yet, the development of this new technology, is not exempt from any controversy. For instance, many observers claim that the expansion of video surveillance poses an unregulated threat to privacy (ACLU, 2021). Still, many people seem to be willing to accept this loss in privacy as the surge in video surveillance makes them feel safer (Madden & Rainie, 2015).

Thereby, throughout this research, the widespread belief that people who have “nothing to hide" should be content with the expansion of CCTV networks as the latter make them safer is challenged (Madden & Rainie, 2015). Indeed, on top of the manifold privacy issues linked with this surge in video surveillance systems, one might legitimately ask the question whether these camera actually make people safer?

The goal of this project is to first investigate the crime deterrent potential of CCTVs in a US city. This potential will also be compared to the different types of crime that are committed. Over a second phase, the dispersion of CCTVs within a city will be investigated. Indeed, according to some researches, mass surveillance has a stronger impact on communities already disadvantaged by their poverty, race, religion, ethnicity, or immigration status (Gellman & Adler-Bell, 2017). We would like to see whether our data enables us to validate or invalidate this theory.

In a world where CCTVs and other surveillance systems are flourishing, it might be good to take a step back and question both the efficacy and the implementation design of such methods often portrayed as miraculous solutions.

# Research questions 

- Does the presence of CCTVs actually deter crime?
- What types of crimes may be deterred by surveillance cameras?
- Is the impact of CCTV installation on crime reduction higher/lower/same in higher income neighborhoods compared to lower income neighborhoods?
- Are there more public cameras in lower income/higher unemployment areas compared to higher income areas? (Does the government respect privacy issues depending on your income level?)
- Do we observe crime displacement issues caused by the installation of CCTV in some neighbourhoods?

# Data source (Augustin, Daniel, Marine)

All data sets were retrieved on local government open data portals (https://data.baltimorecity.gov / https://data.buffalony.gov / https://opendata.dc.gov). We initially found data sets regarding 3 different cities in the United States: Baltimore (MD), Buffalo (NY) and Washington (DC). For each city we found data sets on crimes committed in these respective areas, CCTV locations and neighbourhood metrics. We quickly realised that, for feasibility reasons, we should focus on one city only. As the neighbourhood metrics we found about Washington seemed less complete, we quickly ruled out this option. Using a KML file visualizer and comparing the CCTV locations of Buffalo and Baltimore, we found out that the CCTV data set for Baltimore was more complete. Furthermore, by simply looking at we found some seemingly intriguing patterns. Thus, we finally decided to opt for Baltimore. 

# Data description (Daniel, Augustin, Marine)

- Describe columns/variables
- Describe which type of data
- Describe how clean the provided datasets are?


# Schedule & timeline (Done)

We agreed on meeting on a daily basis (every Thurdays at 0130 PM). The milestones of our project are the following:

21/10 - Thursday meeting at 1:30 PM

1) For each research question, write down exactly the steps which need to be made with the data. Step-by-step (Which variables are important to answering the research question: Then we have 5 manuals in the end, which needed to be executed.)
2) Start tidy datasets (Remove N.As) - We have 3 datasets for Baltimore

28/10 - Thursday meeting at 1:30 PM

1) Start tidy datasets (Remove N.As) - We have 3 datasets for Baltimore
2) Fix bugs/ iterate and ask questions
3) TBD

04/11 - Thursday meeting at 1:30 PM

TBD

10/11 - Project update 

TBD

11/11 - Thursday meeting at 1:30 PM

TBD

18/11 - Thursday meeting at 1:30 PM

TBD

25/11 - Thursday meeting at 1:30 PM

TBD

4/12 - Thursday meeting at 1:30 PM

TBD

11/12 - Thursday meeting at 1:30 PM


15/12 - Final report



