# Analysis {.tabset}

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/setup.R"))
```

### 4.1 Crime VS CCTVs - Does the presence of CCTV deter crime?

First, we create a CCTV_VS_crimes dataset (which basically is a left joint). Next, we are able to plot visually compare the crime rate per area with the density percentage per area. Here we see that there seems to be a trend. 

```{r echo=TRUE}

CCTV_VS_crimes <- CCTV_per_area %>% 
  left_join(CrimeRatePerArea,by="Community")
  
View(CCTV_VS_crimes)

plot(CCTV_VS_crimes$CrimeRatePerArea,CCTV_VS_crimes$density_perc, main="Crime Rate per Community VS CCTV Density per Community",xlab="CrimeRatePerCommunity",ylab="CCTVDensityPerCommunity")

regression <- lm(CCTV_VS_crimes$density_perc~CCTV_VS_crimes$CrimeRatePerArea)
summary(regression)

y<-regression[["coefficients"]][["(Intercept)"]]
x<-regression[["coefficients"]][["CCTV_VS_crimes$CrimeRatePerArea"]]

range <- seq(from=0, to=4.5, by=0.1)

estimation <- x*range+y

lines(range,estimation, col="blue")
```

In order to confirm that perform a regression with the lm-function and call for a summary of the function. Next, the x and y are computed, which are basically the coefficients. Next, we use a trick by creating a range from 0 to 4.5 (because the plot goes ~ from zero to 4.5.) and create a vector. This vector is called estimation. This vector is basically the linear function. So this is the coefficient multiplied by each value in the range plus the intercept. As a result we get the fitted value. The fitted value contains the estimation. After taht we plot the estimation.

In the summary of the regression we see that R^2 (which is the estimator of the goodness of the fit) is pretty poor but still there seems to be a tendency. 





#### 4.1.1 Mapping of CCTVs and crime, felony and misdemeanor rates

In these section we engage with the mapping of the CCTVs and crimes. The method is the same as before with the tmap-package. However, this time we have two different shapes in tm_shape(Baltimore) and tm_shape(balt_dat) which adds the maps togehter (as in ggplot) and over each other. If we take a look at this data we see that it gives an intuition about the data. It seems as if where crime rates are the lowest, there seems to be less CCTVs (for instance in the north area of the city or even in the western CCTVs). There seems to be a correlation between the dark red areas and the CCTV density per area.   

```{r}

Crime_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black")


tmap_mode("view") #Use this command to have interactive maps
baltimore@data[["fid"]]<-baltimore@data[["community"]] #We do that so that we see the name of the Community when using an interactive map
Crime_and_CCTV_map

Felony_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "FelonyRatePerArea", title ="Felony rate per Area in %", style = "quantile") + tm_borders(col="black",alpha=0.3)+ tm_layout(inner.margins = 0.05) + tm_shape(balt_dat) + tm_dots(col="black")


tmap_mode("view") #Use this command to have interactive maps
Felony_and_CCTV_map

Misdemeanor_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "MisdemeanorRatePerArea", title ="Misdemeanor rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3)+ tm_layout(inner.margins = 0.05) + tm_shape(balt_dat) + tm_dots(col="black")


tmap_mode("view") #Use this command to have interactive maps
Misdemeanor_and_CCTV_map

tmap_arrange(Crime_and_CCTV_map,Felony_and_CCTV_map,Misdemeanor_and_CCTV_map)
```
Here we sorted the crime rate per area to find out that the range was. Either using breaks or the automatic style with the quantiles. 

```{r}
sort(baltimore@data[["CrimeRatePerArea"]])

breaks1 <- c(0,0.5,1,1.5,2,2.5,3,3.5,4,4.5) #Not sure what break to use, for the moment I decided to use the automatic break system with the "quantile" parameter


tmap_mode("plot") #We go back to classic plotting

```

#### 4.1.2 Analysis of where crime took place: August 2021

We are trying to see whether the presence of CCTV can deter crime. Here we first try to answer the question where the crime took place (especially in August 2021). We choose AUgust 2021 because it is the latest full month which we have in our dataset. Taking the latest timepoints from the data assures us that most of the CCTVs presented in the dataset were already there (since we have no information of when exactly these CCTVs were added). Again, as before, we create a data table, assign coordinates, define CRS (in this case the CRS is "EPDS4326", which we needed to transform).Again, mapping with tm_shape to get the results. The output shows where crime takes place compared to the CCTV location. 

```{r}

crime_spatial <- as.data.table(crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")))
coordinates(crime_spatial) <-  c("Longitude","Latitude")
proj4string(crime_spatial) <-  CRS("+init=epsg:4326")
crime_spatial <- spTransform(crime_spatial,crs.geo1)

August21Crimes_VS_CCTV <- tm_shape(baltimore) + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.1, title="Crimes committed in August 2021 VS CCTV location",frame.lwd = 5)+ tm_shape(balt_dat) + tm_dots(col="black")+tm_shape(crime_spatial)+tm_dots(col="red",alpha=0.5)

#It could be interesting to see where crime took place relative to CCTV locations in the area with the highest crime rate in August 2021
```

Next, we decided to calculate the crimerate for AUgust per area to see where crime was highest. The results show that they are in midtown (are midtown). 
So following this we will take a closer look at the Midtown area.

```{r}
CrimeRatePerAreaAugust2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")) %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea=(n()/nrow(crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31"))))*100) #We see that midtown is the area with the highest crime rate in August 2021, we might want to focus on that area and see whether there is crime that take place directly next to CCTVs

sum(CrimeRatePerAreaAugust2021$CrimeRatePerArea) #We obtain 100, which is what we expect
```

By using the $st-bbox$ function with their values, which represent the most extreme values on the x-axis and y-axis we can continue with the analysis. So those four values are some geographical values based on coordinate system until we used now (Pseudomercator). And this function assigned that rectangle to be shape file in itself. Now, when we create the midtown map, we can use it as an argument in the tm_shape. THe output is a zoom and the bigger map with a rectangle over the area which we are looking at and analysing. 

```{r}
Midtown_area <-  st_bbox(c(xmin = -8531200.16, xmax = -8527039.15,
                      ymin =4763782.86, ymax = 4766467.70),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Midtown_map <- tm_shape(Midtown_area) + tm_borders(col="white")+ tm_shape(baltimore) + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,title = "Zoom on Midtown Area",title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_symbols(shape = 2, col = "black", size = 0.07)+tm_shape(crime_spatial)+tm_dots(col="red")

Baltimore_map_2 <- tm_shape(baltimore) + tm_borders()+ tm_shape(Midtown_area) + tm_borders(lwd = 1.5,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)


Midtown_map
print(Baltimore_map_2, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain the map with an additional overview

```

#### 4.1.3 Anomaly #1 : Prison

Similar to what we have done before, we first define of what the area of the prison is. It is interesting to analyse the prison and its sourrounding area, since we have many CCTVs around it but basically no crime around it (so it represents an outlier). 

```{r}
tmap_mode("plot")

Prison_area <-  st_bbox(c(xmin = -8529169.92, xmax = -8526465.97,
                      ymin =4764196.55, ymax = 4765056.50),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Prison_map <- tm_shape(Prison_area) + tm_borders(col="black",alpha=0.3)+ tm_shape(baltimore) + tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,title = "Zoom on Baltimore Prison",title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_dots(col="black") #This map zooms on the prison. This "Area" is special. We have no data on crime there, we can also see that the there is a huge concentration of CCTVs directly next to the prison.


Baltimore_map <- tm_shape(baltimore) + tm_borders()+ tm_shape(Prison_area) + tm_borders(lwd = 3,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)


Prison_map
print(Baltimore_map, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain 

```

### 4.2 CCTVs VS Felonies and Misdemeanors - What types of crimes may be deterred by surveillance cameras?

This is exactly the same what we have done for 4.1.. What we want to see whether there is a difference in terms of correlation between felony & misdemeanor and crime. The results shows a weak r^2, and the answer get even worse in terms of correlation graphically. Here, we do not see bigger impact on crime types of CCTV installation. 

```{r}

#Felonies

plot(FelonyStats$FelonyRatePerArea,CCTV_VS_crimes$density_perc, main="Felony Rate per Community VS CCTV Density per Community",xlab="FelonyRatePerCommunity",ylab="CCTVDensityPerCommunity")

regression5 <- lm(CCTV_VS_crimes$density_perc~FelonyStats$FelonyRatePerArea)
summary(regression5) #There is a very poor correlation 

y5<-regression5[["coefficients"]][["(Intercept)"]]
x5<-regression5[["coefficients"]][["FelonyStats$FelonyRatePerArea"]]

range5 <- seq(from=-1, to=5, by=0.1)

estimation5 <- x5*range5+y5

lines(range5,estimation5, col="blue") 

#Misdemeanors

plot(MisdemeanorStats$MisdemeanorRatePerArea,CCTV_VS_crimes$density_perc, main="Misdemeanor Rate per Community VS CCTV Density per Community",xlab="MisdemeanorRatePerCommunity",ylab="CCTVDensityPerCommunity")

regression6 <- lm(CCTV_VS_crimes$density_perc~MisdemeanorStats$MisdemeanorRatePerArea)
summary(regression6) #There is a very poor correlation 

y6<-regression6[["coefficients"]][["(Intercept)"]]
x6<-regression6[["coefficients"]][["MisdemeanorStats$MisdemeanorRatePerArea"]]

range6 <- seq(from=-1, to=6, by=0.1)

estimation6 <- x6*range6+y6

lines(range6,estimation6, col="blue")

```

### 4.3 Comparison of CCTV density and wealth

We went to see whether there is a correlation between CCTV density and wealth. So, similarily, we perform a regression. The results here are not so conclusive, since we have a poor adjusted r^2 and a poor r^2. Visually we can see intersting patterns. If we look at the map we see that at least those areas with no CCTVs are more likely to be quite wealthy. However, we are not sure whether this is the only dependeny here, thus we think it is rather correlated to the crime rate in these areas. Again, in the northern parts we see less CCTV, less crime, and also more wealthier population.

```{r}

plot(CCTV_per_area$density_perc,poverty_data$hhpov19, main="CCTV density VS poverty rate",xlab="CCTV Density",ylab="Poverty rate")

regression2 <- lm(poverty_data$hhpov19~CCTV_per_area$density_perc)
summary(regression2)

y2<-regression2[["coefficients"]][["(Intercept)"]]
x2<-regression2[["coefficients"]][["CCTV_per_area$density_perc"]]

range2 <- seq(from=-5, to=12, by=0.2)

estimation2 <- x2*range2+y2

lines(range2,estimation2, col="blue")

```

#### 4.3.1 Mapping of CCTVs and wealth

We see a tendency. There seems to be more crimes in poorer areas.

```{r}

baltimore$community %in% poverty_data$CSA2010 #We see that we have a perfect match

baltimore@data <- left_join(baltimore@data, poverty_data, by = c('community' = 'CSA2010'))

Wealth_and_CCTV_map <- tm_shape(baltimore)+tm_fill(col = "hhpov19", title ="Poverty rate per Area",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black") #This visualization is particularly interesting. Indeed, while the regression between crime rates and CCTV density was not very conclusive (we obtained a very poor R squared suggesting a poor correlation between poverty and CCTV density), this map might actually explain why we obtained such result and give us interesting hints. Indeed, we see that many CCTVs are located in Downtown/Seton Hill and in Inner Harbor/Federal Hill, namely in the centre of Baltimore and that the poverty rates is very low in these two regions. This makes sense as centers of city are typically not the poorest areas. Yet, what we also see is that many of the least poor region in the "suburbs" often have very low CCTV densities. This might confirm the idea that there tends to be less CCTVs in richer neighbourhoof.


```

### 4.4 Comparison of crimes and wealth

The idea is to find areas which were impacted by a certain type of crime. We see that there was a mainly equal distribution between felony and misdemeanor. We seem to have a strong tendency in downtown - which is at the same time one of the richest areas in Baltimore. Here, we have not enough information to draw conclusions but it could be that there are less felony crimes in this area. 

```{r}

plot(CrimeRatePerArea$CrimeRatePerArea,poverty_data$hhpov19, main="Crime Rate VS poverty rate",xlab="Crime rate",ylab="Poverty rate")

regression3 <- lm(poverty_data$hhpov19~CrimeRatePerArea$CrimeRatePerArea)
summary(regression3)

y3<-regression3[["coefficients"]][["(Intercept)"]]
x3<-regression3[["coefficients"]][["CrimeRatePerArea$CrimeRatePerArea"]]

range3 <- seq(from=-2, to=4.5, by=0.1)

estimation3 <- x3*range3+y3

lines(range3,estimation3, col="blue")
```

### 4.5 Felonies VS Misdemeanors - Do we have an equal crime type distribution?

```{r}

plot(FelonyStats$FelonyRatePerArea,MisdemeanorStats$MisdemeanorRatePerArea,main="Felony VS Misdemeanor", xlab="Felony",ylab="Misdemeanor") #This allows us to see whether Felony and Misdemeanors are correlated. This seems to be the case

regression4 <- lm(FelonyStats$FelonyRatePerArea~MisdemeanorStats$MisdemeanorRatePerArea)
summary(regression4)

y4<-regression4[["coefficients"]][["(Intercept)"]]
x4<-regression4[["coefficients"]][["MisdemeanorStats$MisdemeanorRatePerArea"]]

range4 <- seq(from=-1, to=5, by=0.1)

estimation4 <- x4*range4+y4

lines(range4,estimation4, col="blue")

#Still, we see that there seems ot be some outliers. I don't know if it is relevant but the biggest outlier is Downtown/Seton Hill, is turns out it also is one of the richest area in Baltimore.

```

jgg
### 4.6
* Answers to the research questions
* Different methods considered
* Competing approaches
* Justifications