# Analysis {.tabset}

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("scripts/setup.R"))
```

### 4.1 Crime VS CCTVs - Does the presence of CCTV deter crime?

The idea here is to see whether there is any relationship between crime rates and CCTV density. To do so, we first create a simple linear regression model. We create a new data frame called `CCTV_VS_crimes` (which basically is a left joint). The linear regression indicates a rather weak correlation between higher crime rates and higher CCTV density. The $R2$ is at 35%. Still, plotting the observations enables one to see a tendency. The blue line represent the regression line.

```{r echo=FALSE, results = 'markup'}

CCTV_VS_crimes <- CCTV_per_area %>% 
  left_join(CrimeRatePerArea,by="Community")
  
regression <- lm(CCTV_VS_crimes$density_perc~CCTV_VS_crimes$CrimeRatePerArea)
summary(regression)

ggplot(data=CCTV_VS_crimes,mapping= aes(x=CrimeRatePerArea,y=density_perc)) + 
  labs(title = "Crime Rate per Community VS CCTV Density per Community", x="CrimeRatePerCommunity",y="CCTVDensityPerCommunity")+
  geom_point(shape=1) + 
  geom_smooth(method = lm,color="blue",size=0.3)
```

#### 4.1.1 Mapping of CCTVs and crime, felony and misdemeanor rates

In these section we engage with the mapping of the CCTVs and crimes. The method is the same as before with the `tmap` package. However, this time we have two different shapes: `tm_shape(baltimore)` which constitutes the base map and `tm_shape(balt_dat)` which adds a layer containing points. If we take a look at this map we see that it gives an intuition about the phenomenon we illustrated before. It seems as if where crime rates are the lowest, there seems to be less CCTVs (for instance in the north area of the city or even in the western areas). There seems to be a correlation between the dark red areas and the CCTV per area.   

```{r results='markup'}

Crime_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black")

Felony_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "FelonyRatePerArea", title ="Felony rate per Area in %", style = "quantile") + tm_borders(col="black",alpha=0.3)+ tm_layout(inner.margins = 0.05) + tm_shape(balt_dat) + tm_dots(col="black")

Misdemeanor_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "MisdemeanorRatePerArea", title ="Misdemeanor rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3)+ tm_layout(inner.margins = 0.05) + tm_shape(balt_dat) + tm_dots(col="black")

tmap_mode("view") #Use this command to have interactive maps

baltimore@data[["fid"]]<-baltimore@data[["community"]] #We do that so that we see the name of the Community when using an interactive map

tmap_arrange(Crime_and_CCTV_map,Felony_and_CCTV_map,Misdemeanor_and_CCTV_map)
```


<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>

We are still not sure whether we should use the automatic breaking feature of `tmap` of whether we should set personalized map breaks. The following chunk illustrates how we could create personalized break arguments.


```{r}
sort(baltimore@data[["CrimeRatePerArea"]])

breaks1 <- c(0,0.5,1,1.5,2,2.5,3,3.5,4,4.5) #Not sure what break to use, for the moment I decided to use the automatic break system with the "quantile" parameter

tmap_mode("plot") #We go back to classic plotting
```

#### 4.1.2 Analysis of where crime took place: August 2021

We are still trying to see whether the presence of CCTV can deter crime. One thing that could be interesting is to spatially locate crime and compare it to CCTV location. We know that CCTCs capture activities within 256ft (~2 blocks). We will only select crime committed in August 2021 to have intereprtable data (choosing a larger time frame would make the map unreadable). We choose August 2021 because it is the latest full month which we have in our data set. Taking the latest time points from the data assures us that most of the CCTVs presented in the data set were already there (since we have no information of when exactly these CCTVs were added). Again, as before, we create a data table, assign coordinates, define CRS (in this case the CRS is "EPDS4326", which we needed to transform using `spTransform`). Again, we create a map with `tm_shape` to visualise the results. The output shows where crime takes place compared to the CCTV location. By zooming on the map, we see that some crimes are committed directly in front of CCTVs. Although this is not conclusive evidence, this observation goes against the idea that CCTVs are effective crime deterrents. 

```{r results='markup'}

crime_spatial <- as.data.table(crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")))
coordinates(crime_spatial) <-  c("Longitude","Latitude")
proj4string(crime_spatial) <-  CRS("+init=epsg:4326")
crime_spatial <- spTransform(crime_spatial,crs.geo1)

August21Crimes_VS_CCTV <- tm_shape(baltimore) + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.1, title="Crimes committed in August 2021 VS CCTV location",frame.lwd = 5)+ tm_shape(balt_dat) + tm_dots(col="black")+tm_shape(crime_spatial)+tm_dots(col="red",alpha=0.5)

#It could be interesting to see where crime took place relative to CCTV locations in the area with the highest crime rate in August 2021

tmap_mode("view") #Use this command to have interactive maps
August21Crimes_VS_CCTV
```

Next, we decided to calculate the crime rate for August per area to see where crime was highest. The results show that they are in Midtown. 
So following this we will take a closer look at the Midtown area.

```{r}
CrimeRatePerAreaAugust2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")) %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea=(n()/nrow(crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31"))))*100) #We see that midtown is the area with the highest crime rate in August 2021, we might want to focus on that area and see whether there is crime that take place directly next to CCTVs

sum(CrimeRatePerAreaAugust2021$CrimeRatePerArea) #We obtain 100, which is what we expect
```

By using the `st-bbox` function with their values, which represent the most extreme values on the x-axis and y-axis we can continue with the analysis. So those four values are some geographical values based on coordinate system until we used now (Pseudomercator). And this function assigned that rectangle to be shape file in itself. Now, when we create the midtown map, we can use it as an argument in the tm_shape. The output is a zoom and the bigger map with a rectangle over the area which we are looking at and analysing. 

```{r}
Midtown_area <-  st_bbox(c(xmin = -8531200.16, xmax = -8527039.15,
                      ymin =4763782.86, ymax = 4766467.70),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Midtown_map <- tm_shape(Midtown_area) + tm_borders(col="white")+ tm_shape(baltimore) + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,title = "Zoom on Midtown Area",title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_symbols(shape = 2, col = "black", size = 0.07)+tm_shape(crime_spatial)+tm_dots(col="red")

Baltimore_map_2 <- tm_shape(baltimore) + tm_borders()+ tm_shape(Midtown_area) + tm_borders(lwd = 1.5,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)

tmap_mode("plot")
Midtown_map
print(Baltimore_map_2, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain the map with an additional overview
```

#### 4.1.3 Anomaly #1 : Prison

Similar to what we have done before, we first define of what the area of the prison is. It is interesting to analyse the prison and its sourrounding area, since we have many CCTVs around it but basically no crime around it (so it represents an outlier). 

```{r}
tmap_mode("plot")

Prison_area <-  st_bbox(c(xmin = -8529169.92, xmax = -8526465.97,
                      ymin =4764196.55, ymax = 4765056.50),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Prison_map <- tm_shape(Prison_area) + tm_borders(col="black",alpha=0.3)+ tm_shape(baltimore) + tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,title = "Zoom on Baltimore Prison",title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_dots(col="black") #This map zooms on the prison. This "Area" is special. We have no data on crime there, we can also see that the there is a huge concentration of CCTVs directly next to the prison.


Baltimore_map <- tm_shape(baltimore) + tm_borders()+ tm_shape(Prison_area) + tm_borders(lwd = 3,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)


Prison_map
print(Baltimore_map, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain 
```

### 4.2 CCTVs VS Felonies and Misdemeanors - What types of crimes may be deterred by surveillance cameras?

This is exactly the same what we have done for 4.1.. What we want to see whether there is a difference in terms of correlation between felony & misdemeanor and crime. The results shows a weak $R^2$, and the answer get even worse in terms of correlation graphically. Here, we do not see bigger impact on crime types of CCTV installation. 

```{r echo=FALSE, results = 'markup'}

#Felonies

plot(FelonyStats$FelonyRatePerArea,CCTV_VS_crimes$density_perc, main="Felony Rate per Community VS CCTV Density per Community",xlab="FelonyRatePerCommunity",ylab="CCTVDensityPerCommunity")

regression5 <- lm(CCTV_VS_crimes$density_perc~FelonyStats$FelonyRatePerArea)
summary(regression5) #There is a very poor correlation 

y5<-regression5[["coefficients"]][["(Intercept)"]]
x5<-regression5[["coefficients"]][["FelonyStats$FelonyRatePerArea"]]

range5 <- seq(from=-1, to=5, by=0.1)

estimation5 <- x5*range5+y5

lines(range5,estimation5, col="blue") 

#Misdemeanors

plot(MisdemeanorStats$MisdemeanorRatePerArea,CCTV_VS_crimes$density_perc, main="Misdemeanor Rate per Community VS CCTV Density per Community",xlab="MisdemeanorRatePerCommunity",ylab="CCTVDensityPerCommunity")

regression6 <- lm(CCTV_VS_crimes$density_perc~MisdemeanorStats$MisdemeanorRatePerArea)
summary(regression6) #There is a very poor correlation 

y6<-regression6[["coefficients"]][["(Intercept)"]]
x6<-regression6[["coefficients"]][["MisdemeanorStats$MisdemeanorRatePerArea"]]

range6 <- seq(from=-1, to=6, by=0.1)

estimation6 <- x6*range6+y6

lines(range6,estimation6, col="blue")
```

### 4.3 Comparison of CCTV density and wealth

We went to see whether there is a correlation between CCTV density and wealth. So, similarily, we perform a regression. The results here are not so conclusive, since we have a poor $adjusted R^2$ and a poor $R^2$. Visually we can see intersting patterns. If we look at the map we see that at least those areas with no CCTVs are more likely to be quite wealthy. However, we are not sure whether this is the only dependeny here, thus we think it is rather correlated to the crime rate in these areas. Again, in the northern parts we see less CCTV, less crime, and also more wealthier population.

```{r echo=FALSE, results = 'markup'}

plot(CCTV_per_area$density_perc,poverty_data$hhpov19, main="CCTV density VS poverty rate",xlab="CCTV Density",ylab="Poverty rate")

regression2 <- lm(poverty_data$hhpov19~CCTV_per_area$density_perc)
summary(regression2)

y2<-regression2[["coefficients"]][["(Intercept)"]]
x2<-regression2[["coefficients"]][["CCTV_per_area$density_perc"]]

range2 <- seq(from=-5, to=12, by=0.2)

estimation2 <- x2*range2+y2

lines(range2,estimation2, col="blue")
```

#### 4.3.1 Mapping of CCTVs and wealth

We see a tendency. There seems to be more crimes in poorer areas.

```{r echo=FALSE, results = 'markup'}

baltimore$community %in% poverty_data$CSA2010 #We see that we have a perfect match

baltimore@data <- left_join(baltimore@data, poverty_data, by = c('community' = 'CSA2010'))

Wealth_and_CCTV_map <- tm_shape(baltimore)+tm_fill(col = "hhpov19", title ="Poverty rate per Area",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black") #This visualization is particularly interesting. Indeed, while the regression between crime rates and CCTV density was not very conclusive (we obtained a very poor R squared suggesting a poor correlation between poverty and CCTV density), this map might actually explain why we obtained such result and give us interesting hints. Indeed, we see that many CCTVs are located in Downtown/Seton Hill and in Inner Harbor/Federal Hill, namely in the centre of Baltimore and that the poverty rates is very low in these two regions. This makes sense as centers of city are typically not the poorest areas. Yet, what we also see is that many of the least poor region in the "suburbs" often have very low CCTV densities. This might confirm the idea that there tends to be less CCTVs in richer neighborhood.

tmap_mode("view")
Wealth_and_CCTV_map
```

### 4.4 Comparison of crimes and wealth

The idea is to find areas which were impacted by a certain type of crime. We see that there was a mainly equal distribution between felony and misdemeanor. We seem to have a strong tendency in downtown - which is at the same time one of the richest areas in Baltimore. Here, we have not enough information to draw conclusions but it could be that there are less felony crimes in this area. 

```{r echo=FALSE, results = 'markup'}

plot(CrimeRatePerArea$CrimeRatePerArea,poverty_data$hhpov19, main="Crime Rate VS poverty rate",xlab="Crime rate",ylab="Poverty rate")

regression3 <- lm(poverty_data$hhpov19~CrimeRatePerArea$CrimeRatePerArea)
summary(regression3)

y3<-regression3[["coefficients"]][["(Intercept)"]]
x3<-regression3[["coefficients"]][["CrimeRatePerArea$CrimeRatePerArea"]]

range3 <- seq(from=-2, to=4.5, by=0.1)

estimation3 <- x3*range3+y3

lines(range3,estimation3, col="blue")
```

### 4.5 Felonies VS Misdemeanors - Do we have an equal crime type distribution?

```{r echo=FALSE, results = 'markup'}

plot(FelonyStats$FelonyRatePerArea,MisdemeanorStats$MisdemeanorRatePerArea,main="Felony VS Misdemeanor", xlab="Felony",ylab="Misdemeanor") #This allows us to see whether Felony and Misdemeanors are correlated. This seems to be the case

regression4 <- lm(FelonyStats$FelonyRatePerArea~MisdemeanorStats$MisdemeanorRatePerArea)
summary(regression4)

y4<-regression4[["coefficients"]][["(Intercept)"]]
x4<-regression4[["coefficients"]][["MisdemeanorStats$MisdemeanorRatePerArea"]]

range4 <- seq(from=-1, to=5, by=0.1)

estimation4 <- x4*range4+y4

lines(range4,estimation4, col="blue")

#Still, we see that there seems ot be some outliers. I don't know if it is relevant but the biggest outlier is Downtown/Seton Hill, is turns out it also is one of the richest area in Baltimore.
```

### 4.6 Next steps after feedback on project update

+ Adjust accroding to the feedback 
+ Finalise interpetations and answer research questions
+ Compare results to other researches 
+ Create some more visualisations (if useful and needed)
+ Include Executive summary at the beginning
+ Add additional data if needed
+ Create bibliography