# Exploratory data analysis {.tabset}

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/setup.R"))
```

### 3.1 Calculation of the density of CCTV per community

The original CCTV dataset which we observed had a slight challenge. Although it contained the neighborhood names were not matching the standard neighborhood names. Concludingly, to solve that we involved geospatial counting. 

Our procedure included the following steps. After reading the table and converting the data into a data table, we define what will be the coordinates in the datasets. Here we have several types of coordinates, and we use x and Y. Those coordinates files have an special object included called crs. Crs is basically the coordinate system which is used. 
We continue by defining an object $crs.geo1$ as being the coordinate system which is being used for all our files. Next, we have the $proj4string$ function, to which we assign this crs.geo1 data.

```{r echo=TRUE}
#read in data table
balt_dat <-  fread(file = here::here("data/Baltimore_CCTV_Locations_Crime_Cameras.csv"))

#convert to data table
balt_dat <- as.data.table(balt_dat)

#make data spatial
coordinates(balt_dat) <-  c("X","Y")
crs.geo1 <-  CRS("+proj=merc +a=6378137 +b=6378137 +lat_ts=0 +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs +type=crs")
proj4string(balt_dat) <-  crs.geo1  
```

Then we plot to see the output (as cloud of points which represent all the CCTVs).

```{r}

plot(balt_dat, pch = 20, col = "steelblue") #We can use the plot function to quickly plot the SpatialPointDataFrame that we created. We see a bunch of points which represent the CCTV location in Baltimore.
```

Next, we have to work with the shapefile which is another special file. Basically it is a set of polygons which represent different areas of the city Baltimore. We downloaded this file on the Open Baltimore Portal, read it in and assign this file again to our crs.geo1 coordinate system. In this way we have assured that our files have the same coordinate system.

```{r echo=TRUE}
#read in shapefile of baltimore
baltimore <-  readOGR(dsn = here::here("data/Community_Statistical_Area"), layer = "Community_Statistical_Area") #name of file and object
proj4string(baltimore) <- crs.geo1
```

Again we plot the results. 

```{r echo=TRUE}
#plot
plot(baltimore,main="Spread of CCTVs in different communities of Baltimore")
plot(balt_dat,pch=20, col="steelblue" , add=TRUE) #If we plot these two lines together, what we obtain is a map od baltimore, we the 56 community statistical areas and the CCTVs on top of the map.
```

To illustrate these results verbally, we need R to count for us how many CCTV belongs to which area. Here, the function $over$ counts how many CCTVs are layed over a certain polygon frame. Next, we create a new object calles **counts**, make it into a dataframe (so that it is easier for us to work with it) and using the $sum(countsFreq)$ to ensure that we have 56 observations in total. From the results we see that we have 41 observations, so  there are only 41 out of 56 areas where there are some CCTV. 

```{r echo=TRUE}
#Perform the count
proj4string(balt_dat)
proj4string(baltimore) #To be able to perform the count, we must ensure that the two spatial files have a similar CRS. This is the case as we attributed these two files "crs.geo1" 

res2 <- over(balt_dat,baltimore) #This function tells you to which community each CCTV belongs to
counts <- table(res2$community)
counts <- as.data.frame(counts)
colnames(counts)[1] <- "Community"
sum(counts$Freq) #We see that we have 836 observation in total, this is a good sign as our initial CCTV data set contained 836 obesrvations
```

To make that workable, we need to create a new CCTV file, from which we just add 0 to each N.A.-location. Lastly, we create a new column with the $mutate$-function to calculate the CCTV-density which shows the amount of CCTV per area divided by the total amount of CCTV. 

```{r echo=TRUE}
CCTV_per_area <- area_data[2] %>% 
  left_join(counts,by="Community") #One must add the communities where there are no counts i.e no CCTV

CCTV_per_area[is.na(CCTV_per_area)] <- 0

CCTV_per_area <- mutate(CCTV_per_area, density_perc=(CCTV_per_area$Freq/(sum(CCTV_per_area$Freq)))*100)
```

#### 3.1.1 Mapping of CCTV density

Here we use the piping operator to ensure that the community that we have in the Baltimore dataset are the same as the one we are having in the CCTV per are dataset. As this only returns true values that means that it works and is good for further analysis. 

```{r}
library(tmap)
baltimore$community %in% CCTV_per_area$Community
```

Next, we perform a $left join$ between the Baltimore dataset and the CCTV per are. To hedge against the different writing styles (one time it is written with a capital letter and one time with a small letter), we use the vector in the end. Finally, we create the map with the $tmap package$. The $tmap$ package works as the $ggplot2$ package: First, we need to define an element, it always starts with the tm_shape argument, and then you can add with the plus operator the as many argument as you wish. We used the Baltimore-datasets, filled it with the density percentage, defined some breaks, set the borders and the finally the layout. 

```{r}
baltimore@data <- left_join(baltimore@data, CCTV_per_area, by = c('community' = 'Community'))

CCTV_dens_map <- tm_shape(baltimore) + tm_fill(col = "density_perc", title ="CCTV density per Area in %", breaks=c(0,1,2,3,4,5,6,7,8,9,10,11)) + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

```

### 3.2 Calculation of the crime rate per community

```{r}
CrimeRatePerArea <- crime_data_with_areas %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea=(n()/nrow(crime_data_with_areas))*100)

CrimeRatePerArea <- rbind(CrimeRatePerArea,list("Unassigned -- Jail",0)) #We have no information about crimes committed in jail, yet, the community statistical area encompass 56 area, including jail. In order to ensure consistency, we must add a 56th observation in this data frame.

sum(CrimeRatePerArea$CrimeRatePerArea) #The total sum is 100, which is what we expect
```

#### 3.2.1 Mapping of crime rates

```{r}
library(tmap)

baltimore$community %in% CrimeRatePerArea$Community #We see that we have a perfect match

baltimore@data <- left_join(baltimore@data, CrimeRatePerArea, by = c('community' = 'Community'))

Crime_map <- tm_shape(baltimore) + tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

```

#### 3.2.2 Creation of a distorted map

```{r}

Distorted_Crime_map <- tm_shape(cartogram_ncont(baltimore, "CrimeRatePerArea"))+tm_fill(col = "CrimeRatePerArea", title ="Crime rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.07) #This map distorts the size of each area depending on their respective crime rates. It is interesting as it enables one to see that higher crime rates tends to be concentrated in the city center.

```

### 3.3 Calculation of crime rates by type of crime

```{r}
unique(crime_data_with_areas$Description)

#We see that we have 14 types of crime. We want to observe crimes by types, therefore we want to make new classifications.The law consists of three basic classifications of criminal offenses including infractions, misdemeanors, and felonies. In our data set, we have infractions.

#Misdemeanor:LARCENY FROM AUTO,COMMON ASSAULT, ROBBERY - COMMERCIAL, LARCENY
#Felony: RAPE, ARSON, HOMICIDE, BURGLARY, AUTO THEFT, ROBBERY - CARJACKING, AGG. ASSAULT, ROBBERY - STREET, ROBBERY - RESIDENCE, SHOOTING

crime_cat <- data.frame(Category=c("Misdemeanor","Felony"), Description=c(c("LARCENY FROM AUTO,COMMON ASSAULT,ROBBERY - COMMERCIAL,LARCENY"),c("RAPE,ARSON,HOMICIDE,BURGLARY,AUTO THEFT,ROBBERY - CARJACKING,AGG. ASSAULT,ROBBERY - STREET,ROBBERY - RESIDENCE,SHOOTING")))

crime_cat <- separate_rows(crime_cat, Description, sep = ",")

crime_cat$Description %in% unique(crime_data_with_areas$Description) #Ensure we have a perfect match

crime_data_with_areas <- crime_data_with_areas %>% 
  left_join(crime_cat,by="Description") #We had a new varaible to our crime dataset

CrimePerCategoryPerArea <- crime_data_with_areas %>% 
  group_by(Community,Category) %>%
  summarize(RepartitionPerCategoryPerArea=n())

sum(CrimePerCategoryPerArea$RepartitionPerCategoryPerArea) #Again, we check that we indeed have 349482 observations

CrimeCategoryRepartition <- CrimePerCategoryPerArea %>% 
  group_by(Category) %>% 
  summarise(Repartition=sum(RepartitionPerCategoryPerArea)) #We observe that in Baltimore, the number of felony is close to the number of misdemeanor

FelonyStats <-  CrimePerCategoryPerArea %>% filter(Category=="Felony") %>% 
  mutate(FelonyRatePerArea = (RepartitionPerCategoryPerArea/CrimeCategoryRepartition$Repartition[1])*100)

FelonyStats[56,] <- list("Unassigned -- Jail","Felony",0,0)

MisdemeanorStats <-  CrimePerCategoryPerArea %>% filter(Category=="Misdemeanor") %>% 
  mutate(MisdemeanorRatePerArea = (RepartitionPerCategoryPerArea/CrimeCategoryRepartition$Repartition[2])*100)

MisdemeanorStats[56,] <- list("Unassigned -- Jail","Misdemeanor",0,0)

```

#### 3.3.1 Mapping of felonies and Misdemeanors
```{r}

#Felony

baltimore$community %in% FelonyStats$Community

baltimore@data <- left_join(baltimore@data, FelonyStats, by = c('community' = 'Community'))

Felony_map <- tm_shape(baltimore) + tm_fill(col = "FelonyRatePerArea", title ="Felony rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

#Misdemeanor

baltimore$community %in% MisdemeanorStats$Community

baltimore@data <- left_join(baltimore@data, MisdemeanorStats, by = c('community' = 'Community'))

Misdemeanor_map <- tm_shape(baltimore) + tm_fill(col = "MisdemeanorRatePerArea", title ="Misdemeanor rate per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

```

### 3.4 Calculation of crime evolution
```{r}

Crime_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31"))

Crime_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31"))

Crime_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31"))

Crime_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31"))

Crime_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31"))

Crime_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31"))

Crime_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31"))

Crime_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31"))

crime_data_with_areas %>%  filter(CrimeDateTime < as.Date("2014-01-01")) #We see that we have very few (76) observations before 2014, thus we do not consider them

#_____ Calculations of the crime rates

CrimeRatePerArea2021 <- Crime_in_2021 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2021=(n()/nrow(Crime_in_2021))*100)

CrimeRatePerArea2021 <- rbind(CrimeRatePerArea2021,list("Unassigned -- Jail",0))

CrimeRatePerArea2020 <- Crime_in_2020 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2020=(n()/nrow(Crime_in_2020))*100)

CrimeRatePerArea2020 <- rbind(CrimeRatePerArea2020,list("Unassigned -- Jail",0))

CrimeRatePerArea2019 <- Crime_in_2019 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2019=(n()/nrow(Crime_in_2019))*100)

CrimeRatePerArea2019 <- rbind(CrimeRatePerArea2019,list("Unassigned -- Jail",0))

CrimeRatePerArea2018 <- Crime_in_2018 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2018=(n()/nrow(Crime_in_2018))*100)

CrimeRatePerArea2018 <- rbind(CrimeRatePerArea2018,list("Unassigned -- Jail",0))

CrimeRatePerArea2017 <- Crime_in_2017 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2017=(n()/nrow(Crime_in_2017))*100)

CrimeRatePerArea2017 <- rbind(CrimeRatePerArea2017,list("Unassigned -- Jail",0))

CrimeRatePerArea2016 <- Crime_in_2016 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2016=(n()/nrow(Crime_in_2016))*100)

CrimeRatePerArea2016 <- rbind(CrimeRatePerArea2016,list("Unassigned -- Jail",0))

CrimeRatePerArea2015 <- Crime_in_2015 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2015=(n()/nrow(Crime_in_2015))*100)

CrimeRatePerArea2015 <- rbind(CrimeRatePerArea2015,list("Unassigned -- Jail",0))

CrimeRatePerArea2014 <- Crime_in_2014 %>% 
  group_by(Community) %>%
  summarize(CrimeRatePerArea2014=(n()/nrow(Crime_in_2014))*100)

CrimeRatePerArea2014 <- rbind(CrimeRatePerArea2014,list("Unassigned -- Jail",0))


crime_evolution <- CrimeRatePerArea2021 %>% 
  left_join(CrimeRatePerArea2020,by="Community") %>% 
  left_join(CrimeRatePerArea2019,by="Community") %>%
  left_join(CrimeRatePerArea2018,by="Community") %>%
  left_join(CrimeRatePerArea2017,by="Community") %>% 
  left_join(CrimeRatePerArea2016,by="Community") %>% 
  left_join(CrimeRatePerArea2015,by="Community") %>% 
  left_join(CrimeRatePerArea2014,by="Community")

```



* Mapping out the underlying structure
* Identifying the most important variables
* Univariate visualizations
* Multivariate visualizations
* Summary tables