# Analysis {.tabset}

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("scripts/setup.R"))
```

### 4.1 CCTVs VS Crime - Does the presence of CCTV deter crime?

In order to be in position to comment on the effectiveness of CCTVs on crime deterrence, one is first going to investigate the relationship between CCTV density and crime per capita. To do so, we  create a simple linear regression model. We first create a new data frame called `CCTV_VS_crimes` (which basically is a left joint). The linear regression indicates a moderate correlation between higher CCTV density and higher crime per capita. The $R^2$ is at 42.9%. Plotting the observations enables one to see this tendency. The blue line represents the regression line.

```{r}

CCTV_VS_crimes <- CCTV_per_area %>% 
  left_join(CrimeStatsPerArea,by="Community")
  
regression <- lm(CCTV_VS_crimes$CrimePer1000inhabitants~CCTV_VS_crimes$density_perc)
```
<div align="center">
```{r echo=FALSE,results='asis'}
stargazer(regression,
          title = "Crime VS CCTVs",
          type = "html",
          dep.var.labels="Crime (per 1000 inhabitants)",
          covariate.labels = c("CCTV Density","intercept"))

```
</div>

```{r results='markup'}
ggplot(data=CCTV_VS_crimes,mapping= aes(x=density_perc,y=CrimePer1000inhabitants)) + 
  labs(title = "As CCTV density increases, crime tends to increase as well.", x="CCTV density",y="Crime (per 1000 inhabitants)",)+
  geom_point() + 
  geom_smooth(method = lm,color="blue",size=0.3)
```

#### 4.1.1 Mapping of CCTVs and crime per capita

Another interesting way to illustrate this correlation is by using a map depicting crime per capita in each area and adding an extra layer to represent CCTVs. The method is the same as before with the `tmap` package. However, this time we have two different shapes: `tm_shape(baltimore)` which constitutes the base map and `tm_shape(balt_dat)` which adds a layer containing points. If we take a look at this map we see that it gives an intuition about the phenomenon we illustrated before. It seems as if where crime per capita is the lowest, there seems to be less CCTVs. There seems to be a correlation between the dark red areas and the highest CCTV concentrations. Looking at the north-western and south-western areas of the map, it can be seen that the placement of CCTVs aligns rather well with the areas considered dangerous. We can also use an interactive map. The benefit of using such map is that it enables to get precise information about crime per capita in a given area by clicking on it.


```{r results='markup'}

Crime_per_capita_VS_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "CrimePer1000inhabitants", title ="Crime (per 1000 inhabitants)",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.1, title="Crime seems to be higher in areas with more CCTVs") + tm_shape(balt_dat) + tm_dots(col="black")

tmap_mode("plot")

Crime_per_capita_VS_CCTV_map

```

```{r results='markup'}
baltimore@data[["fid"]]<-baltimore@data[["community"]] #We do that so that we see the name of the Community when using an interactive map

Crime_and_CCTV_map <- tm_shape(baltimore) + tm_fill(col = "CrimePer1000inhabitants", title ="Crime (per 1000 inhabitants)",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black")
```
<div align="center">
This map allows one to see CCTV location precisely and to obtain exact crime per capita figures.
```{r echo=FALSE,results='markup',dpi=72}
tmap_mode("view") #Use this command to have interactive maps

Crime_and_CCTV_map
```
</div>
<br>
However, even though this correlation is interesting and worth mentioning, it does not allow one to say much about the effectiveness of CCTVs. We are stuck in a sort of chicken-and-egg problem. In order to get in position to comment on the crime-deterring potential of CCTVs, we decided to analyse the crime per capita evolution of certain areas in relation with their respective CCTV density. Our goal is to observe how crime per capita behaved since 2014 in areas with high CCTV density compared to areas with low CCTV density. In order to select our areas of interest, we performed a k-means clustering based on two dimensions:  CCTV density and crime per capita. We first scale the data and add the names of each area as row name. We then use the elbow method to determine the optimal number of cluster using `fviz_nbclust`. When performing the kmeans clustering, we specify a nstart parameter. Indeed, if we fail to do so, there is only one choice of random set of rows chosen in the data set as initial centers. We end up with 5 clusters that we represent using `fviz_cluster`. The ratio between the between sum of square and the within sum of square is good (85%), the higher this value the better. Indeed, we want the variation to come from between groups and not within groups.


```{r}
library(FactoMineR)
library(factoextra)

sc.Community_data_Clustering <- scale(Community_data[,c(2:89)]) #We scale the data

row.names(sc.Community_data_Clustering) <- as.vector(t(Community_data[,1])) #We add names of area for each row

fviz_nbclust(sc.Community_data_Clustering[,c(1,3)], kmeans, method="wss")+
  geom_vline(xintercept = 5, linetype = 2) + #add line for better visualisation
  labs(subtitle = "Elbow method")  #We can determine the optimal number of cluster, 5 clusters seems to be reasonable
```
<br><br>
```{r}
set.seed(10)
km.clust2 <- kmeans(sc.Community_data_Clustering[,c(1,3)], 5, nstart = 25)
fviz_cluster(km.clust2, data=sc.Community_data_Clustering[,c(1,3)], repel=TRUE)+labs(x="Crime (per 1000 inhabitants)",y="CCTV density",title = str_wrap(("With 5 clusters, we have a rather good ratio of 85% between between and within SS"),width=65),subtitle=str_wrap(("We will focus on areas in the high crime, high CCTV density cluster as well as those in the lower crime, high CCTV density cluster"),width=80))

```
<br>
We start analysing how crime per capita evolved in areas belonging to the "high crime, high CCTV density" cluster. On top of graphically representing this evolution, one also computes the percentage change in crime per capita betwen 2014 and 2019. We want to see whether we can observe a decreasing tendency in these areas with CCTV density. We create maps using `ggplot` and `geom_line`. Then, in order to show these maps in a more concise way, we use `grid.arrange`. The table below shows the percentage change in crime per capita between the 2014 and the 2019 period. For the sake of our analysis we will only consider the 2014-2019 period. Indeed, it seems reasonable to assume that the decrease one observes in most areas for the 2020 period can be attributed to the Covid-19 pandemic.

```{r results='markup'}

Downtown_Seton_Hill_evolution <- as.vector(t(Community_data[14,c(25,23,21,19,17,15,13)]))

Year <- c(2014:2020)

Downtown_Seton_Hill <- data.frame(Downtown_Seton_Hill_evolution,Year)

Downtown_Seton_Hill_map <- ggplot(Downtown_Seton_Hill,aes(x=Year,y=Downtown_Seton_Hill_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) + 
  labs(title = "Downtown/Seton Hill",x="Year",y="Crime")

Oldtown_Middle_East_evolution <- as.vector(t(Community_data[41,c(25,23,21,19,17,15,13)]))

Oldtown_Middle_East <- data.frame(Oldtown_Middle_East_evolution,Year)

Oldtown_Middle_East_map <- ggplot(Oldtown_Middle_East,aes(x=Year,y=Oldtown_Middle_East_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) + 
  labs(title = "Oldtown/Middle East",x="Year",y="Crime")

Sandtown_Winchester_Harlem_Park_evolution <- as.vector(t(Community_data[47,c(25,23,21,19,17,15,13)]))

Sandtown_Winchester_Harlem_Park <- data.frame(Sandtown_Winchester_Harlem_Park_evolution,Year)

Sandtown_Winchester_Harlem_Park_map <- ggplot(Sandtown_Winchester_Harlem_Park,aes(x=Year,y=Sandtown_Winchester_Harlem_Park_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title = "Sandtown-Winchester/Harlem Park",x="Year",y="Crime")

Cherry_Hill_evolution <- as.vector(t(Community_data[7,c(25,23,21,19,17,15,13)]))

Cherry_Hill <- data.frame(Cherry_Hill_evolution,Year)

Cherry_Hill_map <- ggplot(Cherry_Hill,aes(x=Year,y=Cherry_Hill_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title = "Cherry Hill",x="Year",y="Crime")

library(pdp)

grid.arrange(Downtown_Seton_Hill_map,Oldtown_Middle_East_map,Sandtown_Winchester_Harlem_Park_map,Cherry_Hill_map,nrow=2,ncol=2,top="Four areas with HIGH crime and HIGH CCTV density")

Crime_Evolution_VS_CCTV <- Community_data[,c(1,25,15,4)] %>% 
  mutate(change_perc=((Community_data$CrimePer1000inhabitants19/Community_data$CrimePer1000inhabitants14)-1)*100)

knitr::kable(Crime_Evolution_VS_CCTV[c(7,14,41,47),c(1,5)],col.names = c('Community','Crime per Capita % change')) %>%
  kable_styling(position = "center")

```

One can see that for two out of these four areas with high crime and high CCTV density, crime per capita has actually increased. It slightly decreased for Cherry Hill and decreased more significantly for Sandtown-Winchester/Harlem Park. In order to be able to make a comment on CCTV effectiveness, we decided to also analyse how crime per capita evolved in areas with high crime and low CCTV density.

```{r results='markup'}

Washington_Village_Pigtown_evolution <- as.vector(t(Community_data[54,c(25,23,21,19,17,15,13)]))

Washington_Village_Pigtown_ <- data.frame(Washington_Village_Pigtown_evolution,Year)

Washington_Village_Pigtown_map <- ggplot(Washington_Village_Pigtown_,aes(x=Year,y=Washington_Village_Pigtown_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title = " Washington Village/Pigtown",x="Year",y="Crime")

Harbor_East_Little_Italy_evolution <- as.vector(t(Community_data[26,c(25,23,21,19,17,15,13)]))

Harbor_East_Little_Italy <- data.frame(Harbor_East_Little_Italy_evolution,Year)

Harbor_East_Little_Italy_map <- ggplot(Harbor_East_Little_Italy,aes(x=Year,y=Harbor_East_Little_Italy_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title = "Harbor East/Little Italy",x="Year",y="Crime")

Madison_East_End_evolution <- as.vector(t(Community_data[33,c(25,23,21,19,17,15,13)]))

Madison_East_End <- data.frame(Madison_East_End_evolution,Year)

Madison_East_End_map <- ggplot(Madison_East_End,aes(x=Year,y=Madison_East_End_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title ="Madison East End",x="Year",y="Crime")

Southwest_Baltimore_evolution <- as.vector(t(Community_data[51,c(25,23,21,19,17,15,13)]))

Southwest_Baltimore <- data.frame(Southwest_Baltimore_evolution,Year)

Southwest_Baltimore_map <- ggplot(Southwest_Baltimore,aes(x=Year,y=Southwest_Baltimore_evolution)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 250), breaks =seq(0,250,50)) +
  labs(title ="Southwest Baltimore",x="Year",y="Crime")

grid.arrange(Washington_Village_Pigtown_map,Harbor_East_Little_Italy_map,Madison_East_End_map,Southwest_Baltimore_map,nrow=2,ncol=2,top="Four areas with HIGH crime and LOW CCTV density")

knitr::kable(Crime_Evolution_VS_CCTV[c(26,33,51,54),c(1,5)],col.names = c('Community','Crime per Capita % change')) %>%
  kable_styling(position = "center")

```

When comparing the four members of the high crime, high CCTV density cluster with the four members of the high crime, low CCTV density cluster, we observe that for three members of the low CCTV density cluster, crime per capita has increased while crime per capita has decreased for two members of the high CCTV density cluster. While this could potentially indicate that crime decreased more often in areas with high CCTV density compared to areas with low CCTV density and therefore indicate that CCTV may be effective crime deterrent, it is **absolutely crucial** to temper this statement with statistically significance. Indeed, the decrease we observe in Cherry Hill and Sandtown-Winchester/Harlem Park could be the result of pure luck/coincidence or could be attributed to many other factors. In addition, the extremely small number of data items analysed makes it particularly difficult to draw conclusions.  It should also be noted that although crime has fallen in two high crime, high CCTV areas, in one case it has fallen only slightly (Cherry Hill).

Looking at how crime per capita has evolved throughout Baltimore City, one observes a general downward trend since 2017. This further highlights the fact that the downward results one observes in areas belonging to the HIGH crime, HIGH CCTV density cluster should be interpreted with caution because other factors than CCTVs might be the reason for these decreases. Finally, we computed a simple linear regression model between CCTV density and crime per capita evolution. We found out no significant correlation.

All this leads us to believe that it is difficult to attribute real effectiveness to CCTVs.


```{r results='markup'}

Crime_Yearly_evolution_map <- crime_data_with_areas %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "Overall, crime seems to have decreased for 2017 to 2020 period",subtitle=str_wrap(("This explains why we should be careful when considering CCTV effectiveness"),width=80),x="Year",y="Crime occurences")

Crime_Yearly_evolution_map

regression7 <- lm(Crime_Evolution_VS_CCTV$change_perc~Crime_Evolution_VS_CCTV$density_perc)
```
<br><br>
<div align="center">
```{r echo=FALSE,results='asis'}
stargazer(regression7,
          title = "CCTV density VS Crime evolution",
          type = "html",
          dep.var.labels="Crime per Capita % change",
          covariate.labels = c("CCTV Density","intercept"))
```
</div>
<br><br>

#### 4.1.2 Analysis of where crime took place: August 2021

However, still in an effort to observe how CCTVs impact on crime, we set out to locate crimes committed and compare these locations to those of the surveillance cameras. Knowing that a surveillance camera captures activities within 256ft (~2 blocks), it is interesting to observe whether or not there are "crime-free zones" around the cameras. We will only select crime committed in August 2021 to have interpretable data (choosing a larger time frame would make the map unreadable). We choose August 2021 because it is the latest full month which we have in our data set. Taking the latest time point from the data assures us that most of the CCTVs presented in the data set were already there (since we have no information of when exactly these CCTVs were added). Again, as before, we create a data table, assign coordinates, define CRS (in this case the CRS is "EPDS4326", which we needed to transform using `spTransform`). Again, we create a map with `tm_shape` to visualise the results. The output shows where crime takes place (in red) compared to the CCTV location (in black). By zooming on the map, we see that some crimes are committed directly in front of CCTVs. Although this is not conclusive evidence, this observation goes against the idea that CCTVs are effective crime deterrents. 

```{r results='markup'}

crime_spatial <- as.data.table(crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")))
coordinates(crime_spatial) <-  c("Longitude","Latitude")
proj4string(crime_spatial) <-  CRS("+init=epsg:4326")
crime_spatial <- spTransform(crime_spatial,crs.geo1)

August21Crimes_VS_CCTV <- tm_shape(baltimore) + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.1,frame.lwd = 5)+ tm_shape(balt_dat) + tm_dots(col="black")+tm_shape(crime_spatial)+tm_dots(col="red",alpha=0.5)
```
<div align="center">
Crimes committed in August 2021 (in red) VS CCTVs (in black)
```{r echo=FALSE,results='markup',dpi=72}
tmap_mode("view") #Use this command to have interactive maps
August21Crimes_VS_CCTV
```
</div>
<br>
To further prove that point we decided to focus on one specific area. We arbitrarily decided to focus on the area which had the highest crime incidence in August. Thus, we needed to calculate the crime rate for August per area to see where crime per capita was highest. The results show that they are in Downtown. 

So following this we take a closer look at the Downtown area.

```{r}
CrimePerCapitaPerAreaAugust2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-08-01") & CrimeDateTime <= as.Date("2021-08-31")) %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency=n())

CrimePerCapitaPerAreaAugust2021 <-mutate(CrimePerCapitaPerAreaAugust2021,CrimePer1000inhabitants=((CrimePerCapitaPerAreaAugust2021$CrimeFrequency/population_data$tpop20)*1000))
#We see that Downtown is the area with the highest crime rate in August 2021, we might want to focus on that area and see whether there is crime that take place directly next to CCTVs

```

We create a "sub-map" in the exact same way as we did for the prison in section 3.2.3. In Downtown, we quite clearly see that some crimes (red points) are committed right next to some CCTVs (black triangles).

```{r}
Downtown_area <-  st_bbox(c(xmin = -8531335.08, xmax = -8526873.06,
                      ymin =4765236.47, ymax = 4762527.65),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Downtown_map <- tm_shape(Downtown_area) + tm_borders(col="white")+ tm_shape(baltimore) + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,main.title = "Zoom on Downtown Area",main.title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_symbols(shape = 2, col = "black", size = 0.07)+tm_shape(crime_spatial)+tm_dots(col="red")

Baltimore_map_2 <- tm_shape(baltimore) + tm_borders()+ tm_shape(Downtown_area) + tm_borders(lwd = 1.5,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)

tmap_mode("plot")
Downtown_map
print(Baltimore_map_2, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain the map with an additional overview
```
<br>

The fact that we observe crimes committed right next to surveillance cameras reinforces the hypothesis put forward so far and allows us to answer our first research question once and for all: it does not seem that CCTVs reduce crime.

### 4.2 What types of crimes may be deterred by surveillance cameras?

Although it is impossible to prove the effectiveness of surveillance cameras on crime in general, it is interesting to investigate whether different results are obtained when crime is broken down by type. The methodology we will use is the same as with crime in general.We start with felonies and misdemeanors, then we analyse violent and property crimes.

#### 4.2.1 CCTVs VS Felonies and Misdemeanors

The results of the simple linear regression shows a weak $R^2$ for both felonies and misdemeanors. The correlation between felony and CCTV density and between misdemeanors and CCTV density is roughly the same. Plotting the observations enables one to see this (weak) tendency. The blue line represents the regression line. 


```{r}

#Felonies

CCTV_VS_Felony <- CCTV_per_area %>% 
  left_join(FelonyStats,by="Community")

regression5 <- lm(CCTV_VS_Felony$FelonyPerCapitaPerArea~CCTV_VS_Felony$density_perc)
```
<div align="center">
```{r echo=FALSE, results = 'asis'}

stargazer(regression5,
          title = "CCTV vs Felony",
          type = "html",
          dep.var.labels="Felony (per 1000 inhabitants",
          covariate.labels = c("CCTV Density","intercept"))
```
</div>
<br><br>
```{r results='markup'}
ggplot(data=CCTV_VS_Felony,mapping= aes(x=density_perc,y=FelonyPerCapitaPerArea)) + 
  labs(title = "As CCTV density increases, felony tends to increase as well.", x="CCTV Density ",y="Felony")+
  geom_point() + 
  geom_smooth(method = lm,color="blue",size=0.3)
```


```{r}
#Misdemeanors

CCTV_VS_misdemeanors <- CCTV_per_area %>% 
  left_join(MisdemeanorStats,by="Community")

regression6 <- lm(CCTV_VS_misdemeanors$MisdemeanorPerCapitaPerArea~CCTV_VS_misdemeanors$density_perc)
```
<div align="center">
```{r echo=FALSE, results = 'asis'}
stargazer(regression6,
          title = "CCTV vs Misdemeanor",
          type = "html",
          dep.var.labels="Misdemeanor (per 1000 inhabitants)",
          covariate.labels = c("CCTV Density","intercept"))
```
</div>
<br><br>
```{r results='markup'}
ggplot(data=CCTV_VS_misdemeanors,mapping= aes(x=density_perc,y=MisdemeanorPerCapitaPerArea)) + 
   labs(title = str_wrap(("As CCTV density increases, misdemeanor tends to increase as well."),width = 60), x="CCTV Density ",y="Misdemeanor")+
  geom_point() + 
  geom_smooth(method = lm,color="blue",size=0.3)
```

We are in the exact same situation as with crime. In order to comment on the effectiveness of CCTVs on felonies and/or misdemeanors, we must analyse felony/misdemeanor evolution over time in areas with/without CCTVs. We start with felonies. 

```{r results = 'markup'}

fviz_nbclust(sc.Community_data_Clustering[,c(5,3)], kmeans, method="wss")+
  geom_vline(xintercept = 5, linetype = 2) + # add line for better visualisation
  labs(subtitle = "Elbow method")  #We can determine the optimal number of cluster, 5 clusters seems to be reasonable
```
<br><br>
```{r results = 'markup'}
set.seed(40)
km.clust5 <- kmeans(sc.Community_data_Clustering[,c(5,3)], 5, nstart = 25) #It is important to specify a nstart parameter. Indeed, if we fail to do so, there is only one choice of random set of rows chosen in the dataset as initial centers.

fviz_cluster(km.clust5, data=sc.Community_data_Clustering[,c(5,3)], repel=TRUE) + labs(x="Felony per capita",y="CCTV density",title = str_wrap(("With 5 clusters, we have a rather good ratio of 87.1% between between and within SS"),width=65),subtitle=str_wrap(("We will focus on areas in the high felony, high CCTV density cluster as well as those in the lower felony, high CCTV density cluster"),width=80))
```
<br>
```{r results = 'markup'}

Downtown_Seton_Hill_evolution_Felony <- as.vector(t(Community_data[14,c(73,71,69,67,65,63,61)]))

Downtown_Seton_Hill_Felony <- data.frame(Downtown_Seton_Hill_evolution_Felony,Year)

Downtown_Seton_Hill_map_Felony <- ggplot(Downtown_Seton_Hill_Felony,aes(x=Year,y=Downtown_Seton_Hill_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Downtown/Seton Hill",x="Year",y="Felony")

Sandtown_Winchester_Harlem_Park_evolution_Felony <- as.vector(t(Community_data[47,c(73,71,69,67,65,63,61)]))

Sandtown_Winchester_Harlem_Park_Felony <- data.frame(Sandtown_Winchester_Harlem_Park_evolution_Felony,Year)

Sandtown_Winchester_Harlem_Park_map_Felony <- ggplot(Sandtown_Winchester_Harlem_Park_Felony,aes(x=Year,y=Sandtown_Winchester_Harlem_Park_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Sandtown-Winchester/Harlem Park",x="Year",y="Felony")

Oldtown_Middle_East_evolution_Felony <- as.vector(t(Community_data[41,c(73,71,69,67,65,63,61)]))

Oldtown_Middle_East_Felony <- data.frame(Oldtown_Middle_East_evolution_Felony,Year)

Oldtown_Middle_East_map_Felony <- ggplot(Oldtown_Middle_East_Felony,aes(x=Year,y=Oldtown_Middle_East_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Oldtown/Middle East",x="Year",y="Felony")

Cherry_Hill_evolution_Felony <- as.vector(t(Community_data[7,c(73,71,69,67,65,63,61)]))

Cherry_Hill_Felony <- data.frame(Cherry_Hill_evolution_Felony,Year)

Cherry_Hill_map_Felony <- ggplot(Cherry_Hill_Felony,aes(x=Year,y=Cherry_Hill_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Cherry Hill",x="Year",y="Felony")

grid.arrange(Downtown_Seton_Hill_map_Felony,Sandtown_Winchester_Harlem_Park_map_Felony,Oldtown_Middle_East_map_Felony,Cherry_Hill_map_Felony,nrow=2,ncol=2,top="Four areas with HIGH felony and HIGH CCTV density")

Felony_Evolution_VS_CCTV <- Community_data[,c(1,63,73,4)] %>% 
  mutate(change_perc=((Community_data$FelonyPer1000inhabitants19/Community_data$FelonyPer1000inhabitants14)-1)*100)

knitr::kable(Felony_Evolution_VS_CCTV[c(7,14,41,47),c(1,5)],col.names = c('Community','Felony per Capita % change')) %>%
  kable_styling(position = "center")
```
<br><br>
```{r results = 'markup'}

Poppleton_evolution_Felony <- as.vector(t(Community_data[46,c(73,71,69,67,65,63,61)]))

Poppleton_Felony <- data.frame(Poppleton_evolution_Felony,Year)

Poppleton_map_Felony <- ggplot(Poppleton_Felony,aes(x=Year,y=Poppleton_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Poppleton/The Terraces/Hollins Market",x="Year",y="Felony")

Madison_East_End_evolution_Felony <- as.vector(t(Community_data[33,c(73,71,69,67,65,63,61)]))

Madison_East_End_Felony <- data.frame(Madison_East_End_evolution_Felony,Year)

Madison_East_End_map_Felony <- ggplot(Madison_East_End_Felony,aes(x=Year,y=Madison_East_End_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Madinson/East End",x="Year",y="Felony")

Clifton_Berea_evolution_Felony <- as.vector(t(Community_data[10,c(73,71,69,67,65,63,61)]))

Clifton_Berea_Felony <- data.frame(Clifton_Berea_evolution_Felony,Year)

Clifton_Berea_map_Felony <- ggplot(Clifton_Berea_Felony,aes(x=Year,y=Clifton_Berea_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Clifton-Berea",x="Year",y="Felony")

Midway_Coldstream_evolution_Felony <- as.vector(t(Community_data[36,c(73,71,69,67,65,63,61)]))

Midway_Coldstream_Felony <- data.frame(Midway_Coldstream_evolution_Felony,Year)

Midway_Coldstream_map_Felony <- ggplot(Midway_Coldstream_Felony,aes(x=Year,y=Midway_Coldstream_evolution_Felony)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Midway/Coldstream",x="Year",y="Felony")

grid.arrange(Poppleton_map_Felony,Madison_East_End_map_Felony,Clifton_Berea_map_Felony,Midway_Coldstream_map_Felony,nrow=2,ncol=2,top="Four areas with HIGH felony and LOW CCTV density")

knitr::kable(Felony_Evolution_VS_CCTV[c(10,33,36,46),c(1,5)],col.names = c('Community','Felony per Capita % change')) %>%
  kable_styling(position = "center")

```

We see that in both clusters, felony has increased for three out of four members, regardless of CCTV density. This might indicate that CCTVs are not effective when it comes to felonies either. By plotting the felony evolution over time in Baltimore, we  observe that felony has also slightly increased comparing the 2014 and the 2019 level. Again, it makes it difficult to interpret these results as they are not statistically significant. Still, computing a regression between CCTV density and felony per capita gives the intuition that there only exists a very weak correlation between CCTV density and felony per capita, suggesting that surveillance cameras are not effective in preventing felonies either.

```{r results='markup'}

Felony_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(Category=="Felony") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = str_wrap(("Comparing the 2014 felony level with the 2019 felony level, one observes that felony has slightly increased"),width=65),subtitle=str_wrap(("This further explains why we should be careful when considering CCTV effectiveness in deterring felonies"),width=80),x="Year",y="Felony occurences")

Felony_Yearly_evolution_map
```
<br><br>
<div align="center">
```{r echo=FALSE,results='asis'}
regression10 <- lm(Felony_Evolution_VS_CCTV$change_perc~Felony_Evolution_VS_CCTV$density_perc)
stargazer(regression10,
          title = "CCTV density VS Felony evolution",
          type = "html",
          dep.var.labels="Felony per Capita % change",
          covariate.labels = c("CCTV Density","intercept"))

```
</div>
<br>

We continue with misdemeanors. We do the exact same thing.

```{r results = 'markup'}

fviz_nbclust(sc.Community_data_Clustering[,c(6,3)], kmeans, method="wss")+
  geom_vline(xintercept = 5, linetype = 2) + # add line for better visualisation
  labs(subtitle = "Elbow method")  #We can determine the optimal number of cluster, 5 clusters seems to be reasonable
```
<br><br>
```{r results = 'markup'}
set.seed(50)
km.clust6 <- kmeans(sc.Community_data_Clustering[,c(6,3)], 5, nstart = 25) #It is important to specify a nstart parameter. Indeed, if we fail to do so, there is only one choice of random set of rows chosen in the dataset as initial centers.
fviz_cluster(km.clust6, data=sc.Community_data_Clustering[,c(6,3)], repel=TRUE) + labs(x="Misdemeanor per capita",y="CCTV density",title = str_wrap(("With 5 clusters, we have a rather good ratio of 84.41% between between and within SS"),width=65),subtitle=str_wrap(("We will focus on areas in the high misdemeanor, high CCTV density cluster as well as those in the lower misdemeanor, high CCTV density cluster"),width=80))
```
<br>
```{r results = 'markup'}
Downtown_Seton_Hill_evolution_Misdemeanor <- as.vector(t(Community_data[14,c(89,87,85,83,81,79,77)]))

Downtown_Seton_Hill_Misdemeanor <- data.frame(Downtown_Seton_Hill_evolution_Misdemeanor,Year)

Downtown_Seton_Hill_map_Misdemeanor <- ggplot(Downtown_Seton_Hill_Misdemeanor,aes(x=Year,y=Downtown_Seton_Hill_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Downtown/Seton Hill",x="Year",y="Misdemeanor")

Oldtown_Middle_East_evolution_Misdemeanor <- as.vector(t(Community_data[41,c(89,87,85,83,81,79,77)]))

Oldtown_Middle_East_Misdemeanor <- data.frame(Oldtown_Middle_East_evolution_Misdemeanor,Year)

Oldtown_Middle_East_map_Misdemeanor <- ggplot(Oldtown_Middle_East_Misdemeanor,aes(x=Year,y=Oldtown_Middle_East_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Oldtown/Middle East",x="Year",y="Misdemeanor")

Upton_Druid_Heights_evolution_Misdemeanor <- as.vector(t(Community_data[53,c(89,87,85,83,81,79,77)]))

Upton_Druid_Heights_Misdemeanor <- data.frame(Upton_Druid_Heights_evolution_Misdemeanor,Year)

Upton_Druid_Heights_map_Misdemeanor <- ggplot(Upton_Druid_Heights_Misdemeanor,aes(x=Year,y=Upton_Druid_Heights_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Upton/Druid Heights",x="Year",y="Misdemeanor")

Sandtown_Winchester_Harlem_Park_evolution_Misdemeanor <- as.vector(t(Community_data[47,c(89,87,85,83,81,79,77)]))

Sandtown_Winchester_Harlem_Park_Misdemeanor <- data.frame(Sandtown_Winchester_Harlem_Park_evolution_Misdemeanor,Year)

Sandtown_Winchester_Harlem_Park_map_Misdemeanor <- ggplot(Sandtown_Winchester_Harlem_Park_Misdemeanor,aes(x=Year,y=Sandtown_Winchester_Harlem_Park_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Sandtown-Winchester/Harlem-Park",x="Year",y="Misdemeanor")

grid.arrange(Downtown_Seton_Hill_map_Misdemeanor,Oldtown_Middle_East_map_Misdemeanor,Upton_Druid_Heights_map_Misdemeanor,Sandtown_Winchester_Harlem_Park_map_Misdemeanor,nrow=2,ncol=2,top="Four areas with HIGH misdemeanor and HIGH CCTV density")

Misdemeanor_Evolution_VS_CCTV <- Community_data[,c(1,79,89,4)] %>% 
  mutate(change_perc=((Community_data$MisdemeanorPer1000inhabitants19/Community_data$MisdemeanorPer1000inhabitants14)-1)*100)

knitr::kable(Misdemeanor_Evolution_VS_CCTV[c(14,41,47,53),c(1,5)],col.names = c('Community','Misdemeanor per Capita % change')) %>% kable_styling(position = "center")
```
<br><br>
```{r results = 'markup'}

Washington_Village_Pigtown_evolution_Misdemeanor <- as.vector(t(Community_data[54,c(89,87,85,83,81,79,77)]))

Washington_Village_Pigtown_Misdemeanor <- data.frame(Washington_Village_Pigtown_evolution_Misdemeanor,Year)

Washington_Village_Pigtown_map_Misdemeanor <- ggplot(Washington_Village_Pigtown_Misdemeanor,aes(x=Year,y=Washington_Village_Pigtown_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Washington Village/Pigtown",x="Year",y="Misdemeanor")

Harbor_East_Little_Italy_evolution_Misdemeanor <- as.vector(t(Community_data[26,c(89,87,85,83,81,79,77)]))

Harbor_East_Little_Italy_Misdemeanor <- data.frame(Harbor_East_Little_Italy_evolution_Misdemeanor,Year)

Harbor_East_Little_Italy_map_Misdemeanor <- ggplot(Harbor_East_Little_Italy_Misdemeanor,aes(x=Year,y=Harbor_East_Little_Italy_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Harbor East/Little Italy",x="Year",y="Misdemeanor")

Canton_evolution_Misdemeanor <- as.vector(t(Community_data[5,c(89,87,85,83,81,79,77)]))

Canton_Misdemeanor <- data.frame(Canton_evolution_Misdemeanor,Year)

Canton_map_Misdemeanor <- ggplot(Canton_Misdemeanor,aes(x=Year,y=Canton_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Canton",x="Year",y="Misdemeanor")

Penn_North_Reservoir_Hill_evolution_Misdemeanor <- as.vector(t(Community_data[44,c(89,87,85,83,81,79,77)]))

Penn_North_Reservoir_Hill_Misdemeanor <- data.frame(Penn_North_Reservoir_Hill_evolution_Misdemeanor,Year)

Penn_North_Reservoir_Hill_map_Misdemeanor <- ggplot(Penn_North_Reservoir_Hill_Misdemeanor,aes(x=Year,y=Penn_North_Reservoir_Hill_evolution_Misdemeanor)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 150), breaks =seq(0,150,25)) + 
  labs(title = "Penn North/Reservoir Hill",x="Year",y="Misdemeanor")

grid.arrange(Washington_Village_Pigtown_map_Misdemeanor,Harbor_East_Little_Italy_map_Misdemeanor,Canton_map_Misdemeanor,Penn_North_Reservoir_Hill_map_Misdemeanor,nrow=2,ncol=2,top="Four areas with HIGH misdemeanor and LOW CCTV density")

knitr::kable(Misdemeanor_Evolution_VS_CCTV[c(5,26,44,54),c(1,5)],col.names = c('Community','Misdemeanor per Capita % change')) %>%
  kable_styling(position = "center")

```

Misdemenaors have decreased more often in areas belonging to the low CCTV density cluster. Again, this could potentially suggest that surveillance cameras are not very effective in reducing misdemeanors. Moreover, there is a downward trend in terms of the number of crimes in the whole city. However, these results should be taken with caution as, again, they are not statistically significant and could be due to chance. In order to get a better overall picture of the relationship between CCTV density and misdemeanor per capita, we performed a regression between CCTV density and misdemeanor change. The correlation between the two variables is very weak, suggesting once again that surveillance cameras are ineffective against misdemeanors.

```{r results='markup'}

Misdemeanor_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(Category=="Misdemeanor") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "In Baltimore, Misdemeanor started to decrease as from 2017",subtitle=str_wrap(("This explains why we should be careful when considering CCTV effectiveness in deterring misdemenors"),width=75),x="Year",y="Misdemeanor occurences")

Misdemeanor_Yearly_evolution_map
```

<div align="center">
```{r echo=FALSE,results='asis'}
regression11 <- lm(Misdemeanor_Evolution_VS_CCTV$change_perc~Misdemeanor_Evolution_VS_CCTV$density_perc)
stargazer(regression11,
          title = "CCTV density VS Misdemeanor evolution",
          type = "html",
          dep.var.labels="Misdemeanor per Capita % change",
          covariate.labels = c("CCTV Density","intercept"))

```
</div>
<br><br>

#### 4.2.2 CCTVs VS Violent and Property Crime

It seems that the severity of the crime (i. e. whether it is a felony or a misdemeanor) does not influence the crime-deterring potential of CCTVs. It is now interesting to see whether we observe a difference when decomposing crime into violent and property crime. We first perform one simple linear regression between CCTV density and violent crime and another between CCTV density and property crime. The first interesting thing one can observe is that we observe a much stronger correlation between between CCTV density and violent crime than between CCTV density and property crime. The $R^2$ of the first regression is at 51.5%, more than any other $R^2$ obtained until now. This suggests that violent crime per capita is a considerable determinant of CCTV density.

```{r results = 'markup'}

CCTV_VS_ViolentCrime <- CCTV_per_area %>% 
  left_join(ViolentStats,by="Community")

regression21 <- lm(CCTV_VS_ViolentCrime$ViolentCrimePerCapitaPerArea~CCTV_VS_ViolentCrime$density_perc)
```
<div align="center">
```{r echo=FALSE,results = 'asis'}
stargazer(regression21,
          title = "CCTV vs Violent Crime",
          type = "html",
          dep.var.labels="Violent Crime (per 1000 inhabitants)",
          covariate.labels = c("CCTV Density","intercept"))
```
</div>
<br><br>
```{r results = 'markup'}
ggplot(Community_data,aes(x=density_perc,y=ViolentCrimePerCapitaPerArea))+
  geom_point()+
   geom_smooth(method = lm,color="blue",size=0.3)+
  labs(x="CCTV Density per Area",y="Violent crime (per 1000 inhabitants)",title="Violent crime increases with CCTV density",subtitle = str_wrap("Yet, we observe that the lack of data about CCTV in some areas might influence our results."),width=45)
```
<br><br>
```{r results = 'markup'}
CCTV_VS_PropertyCrime <- CCTV_per_area %>% 
  left_join(PropertyStats,by="Community")

regression22 <- lm(CCTV_VS_PropertyCrime$PropertyCrimePerCapitaPerArea~CCTV_VS_PropertyCrime$density_perc)
```
<div align="center">
```{r echo=FALSE,results = 'asis'}
stargazer(regression22,
          title = "CCTV vs Property Crime",
          type = "html",
          dep.var.labels="Property Crime (per 1000 inhabitants)",
          covariate.labels = c("CCTV Density","intercept"))

#We observe a stronger correlation between Violent Crime and CCTV density compared to Property crime and CCTV density
```
</div>
<br><br>
```{r results = 'markup'}
ggplot(Community_data,aes(x=density_perc,y=PropertyCrimePerCapitaPerArea))+
  geom_point()+
   geom_smooth(method = lm,color="blue",size=0.3)+
  labs(x="CCTV Density per Area",y="Property crime (per 1000 inhabitants)",title="Property crime is weakly correlated with CCTV intensity",subtitle = str_wrap("The correlation is weaker than between violent crime and CCTV density"),width=45)

```

Yet, as in past sections, we have to analyse how violent and property crime evolved over time in areas with different CCTV densities to be in position to comment on CCTV effectiveness. We start with violent crime.

```{r results = 'markup'}

fviz_nbclust(sc.Community_data_Clustering[,c(7,3)], kmeans, method="wss")+
  geom_vline(xintercept = 5, linetype = 2) + # add line for better visualisation
  labs(subtitle = "Elbow method")  #We can determine the optimal number of cluster, 5 clusters seems to be reasonable
```
<br><br>
```{r results = 'markup'}
set.seed(20)
km.clust3 <- kmeans(sc.Community_data_Clustering[,c(7,3)], 5, nstart = 25) #It is important to specify a nstart parameter. Indeed, if we fail to do so, there is only one choice of random set of rows chosen in the dataset as initial centers.
fviz_cluster(km.clust3, data=sc.Community_data_Clustering[,c(7,3)], repel=TRUE) + labs(x="Violent crime per capita",y="CCTV density",title = str_wrap(("With 5 clusters, we have a good ratio of 87.4% between between and within SS"),width=65),subtitle=str_wrap(("We will focus on areas in the high violent crime, high CCTV density cluster as well as those in the lower violent crime, high CCTV density cluster"),width=80))
```
<br><br>
```{r results = 'markup'}
Downtown_Seton_Hill_evolution_Violent <- as.vector(t(Community_data[14,c(41,39,37,35,33,31,29)]))

Downtown_Seton_Hill_Violent <- data.frame(Downtown_Seton_Hill_evolution_Violent,Year)

Downtown_Seton_Hill_map_Violent <- ggplot(Downtown_Seton_Hill_Violent,aes(x=Year,y=Downtown_Seton_Hill_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Downtown/Seton Hill",x="Year",y="Violent Crime")

Oldtown_Middle_East_evolution_Violent <- as.vector(t(Community_data[41,c(41,39,37,35,33,31,29)]))

Oldtown_Middle_East_Violent <- data.frame(Oldtown_Middle_East_evolution_Violent,Year)

Oldtown_Middle_East_map_Violent <- ggplot(Oldtown_Middle_East_Violent,aes(x=Year,y=Oldtown_Middle_East_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Oldtown/Middle East",x="Year",y="Violent Crime")

Sandtown_Winchester_Harlem_Park_evolution_Violent <- as.vector(t(Community_data[47,c(41,39,37,35,33,31,29)]))

Sandtown_Winchester_Harlem_Park_Violent <- data.frame(Sandtown_Winchester_Harlem_Park_evolution_Violent,Year)

Sandtown_Winchester_Harlem_Park_map_Violent <- ggplot(Sandtown_Winchester_Harlem_Park_Violent,aes(x=Year,y=Sandtown_Winchester_Harlem_Park_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Sandtown-Winchester/Harlem Park",x="Year",y="Violent Crime")

Cherry_Hill_evolution_Violent <- as.vector(t(Community_data[7,c(41,39,37,35,33,31,29)]))

Cherry_Hill_Violent <- data.frame(Cherry_Hill_evolution_Violent,Year)

Cherry_Hill_map_Violent <- ggplot(Cherry_Hill_Violent,aes(x=Year,y=Cherry_Hill_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Cherry Hill",x="Year",y="Violent Crime")

library(pdp)

grid.arrange(Downtown_Seton_Hill_map_Violent,Oldtown_Middle_East_map_Violent,Sandtown_Winchester_Harlem_Park_map_Violent,Cherry_Hill_map_Violent,nrow=2,ncol=2,top="Four areas with HIGH violent crime and HIGH CCTV density")

Violent_Crime_Evolution_VS_CCTV <- Community_data[,c(1,31,41,4)] %>% 
  mutate(change_perc=((Community_data$ViolentCrimePer1000inhabitants19/Community_data$ViolentCrimePer1000inhabitants14)-1)*100)

Violent_Crime_Evolution_VS_CCTV[c(7,14,41,47),c(-3)]

knitr::kable(Violent_Crime_Evolution_VS_CCTV[c(7,14,41,47),c(1,5)],col.names = c('Community','Violent Crime per Capita % change')) %>% kable_styling(position = "center")

```
<br><br>
```{r results = 'markup'}
Clifton_Berea_evolution_Violent <- as.vector(t(Community_data[10,c(41,39,37,35,33,31,29)]))

Clifton_Berea_Violent <- data.frame(Clifton_Berea_evolution_Violent,Year)

Clifton_Berea_map_Violent <- ggplot(Clifton_Berea_Violent,aes(x=Year,y=Clifton_Berea_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Clifton-Berea",x="Year",y="Violent Crime")

Pimlico_Arlington_Hilltop_evolution_Violent <- as.vector(t(Community_data[45,c(41,39,37,35,33,31,29)]))

Pimlico_Arlington_Hilltop_Violent <- data.frame(Pimlico_Arlington_Hilltop_evolution_Violent,Year)

Pimlico_Arlington_Hilltop_map_Violent <- ggplot(Pimlico_Arlington_Hilltop_Violent,aes(x=Year,y=Pimlico_Arlington_Hilltop_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Pimlico/Arlington/Hilltop",x="Year",y="Violent Crime")

Midway_Coldstream_evolution_Violent <- as.vector(t(Community_data[36,c(41,39,37,35,33,31,29)]))

Midway_Coldstream_Violent <- data.frame(Midway_Coldstream_evolution_Violent,Year)

Midway_Coldstream_map_Violent <- ggplot(Midway_Coldstream_Violent,aes(x=Year,y=Midway_Coldstream_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Midway/Coldstream",x="Year",y="Violent Crime")

Madison_East_End_evolution_Violent <- as.vector(t(Community_data[33,c(41,39,37,35,33,31,29)]))

Madison_East_End_Violent <- data.frame(Madison_East_End_evolution_Violent,Year)

Madison_East_End_map_Violent <- ggplot(Madison_East_End_Violent,aes(x=Year,y=Madison_East_End_evolution_Violent)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Madison/East End",x="Year",y="Violent Crime")

grid.arrange(Clifton_Berea_map_Violent,Pimlico_Arlington_Hilltop_map_Violent,Midway_Coldstream_map_Violent,Madison_East_End_map_Violent,nrow=2,ncol=2,top="Four areas with HIGH violent crime and LOW CCTV density")

knitr::kable(Violent_Crime_Evolution_VS_CCTV[c(10,33,36,45),c(1,5)],col.names = c('Community','Violent Crime per Capita % change')) %>% kable_styling(position = "center")

```

This time, it is in the group of areas with the highest concentration of cameras that violent crime has fallen most often. However, before jumping to conclusions, it is worth mentioning that only one neighbourhood in this group has decreased and that, as usual, this result could be due to luck. It should also be noted that overall, violent crime in Baltimore has increased. The simple linear regression performed between CCTV density and violent crime evolution do not indicate any correlation between the two variables, thus leading us to the conclusion that CCTVs do not seem to be effective in reducing violent crime etiher.

```{r results='markup'}

Violent_Crime_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(VIO_PROP_CFS=="VIOLENT") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = str_wrap(("Overall, violent crime has increased in Baltimore over the 2014-2019 period"),width=65),x="Year",y="Violent crime occurences")

Violent_Crime_Yearly_evolution_map

regression8 <- lm(Violent_Crime_Evolution_VS_CCTV$change_perc~Violent_Crime_Evolution_VS_CCTV$density_perc)
```
<div align="center">

```{r echo=FALSE, results='asis'}
stargazer(regression8,
          title = "CCTV density VS Violent Crime evolution",
          type = "html",
          dep.var.labels="Violent Crime per Capita % change",
          covariate.labels = c("CCTV Density","intercept"))

```
</div>
<br>
The last type of crime we must consider is property crime.

```{r results = 'markup'}

fviz_nbclust(sc.Community_data_Clustering[,c(8,3)], kmeans, method="wss")+
  geom_vline(xintercept = 5, linetype = 2) + # add line for better visualisation
  labs(subtitle = "Elbow method")  #We can determine the optimal number of cluster, 5 clusters seems to be reasonable
```
<br><br>
```{r results = 'markup'}
set.seed(30)
km.clust4 <- kmeans(sc.Community_data_Clustering[,c(8,3)], 5, nstart = 25) #It is important to specify a nstart parameter. Indeed, if we fail to do so, there is only one choice of random set of rows chosen in the dataset as initial centers.
fviz_cluster(km.clust4, data=sc.Community_data_Clustering[,c(8,3)], repel=TRUE) + labs(x="Property crime per capita",y="CCTV density",title = str_wrap(("With 5 clusters, we have a rather good ratio of 82.8% between between and within SS"),width=65),subtitle=str_wrap(("We will focus on areas in the high property crime, high CCTV density cluster as well as those in the lower property crime, high CCTV density cluster"),width=80))
```
<br><br>
```{r results = 'markup'}
Downtown_Seton_Hill_evolution_Property <- as.vector(t(Community_data[14,c(57,55,53,51,49,47,45)]))

Downtown_Seton_Hill_Property <- data.frame(Downtown_Seton_Hill_evolution_Property,Year)

Downtown_Seton_Hill_map_Property <- ggplot(Downtown_Seton_Hill_Property,aes(x=Year,y=Downtown_Seton_Hill_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Downtown/Seton Hill",x="Year",y="Property Crime")

Oldtown_Middle_East_evolution_Property <- as.vector(t(Community_data[41,c(57,55,53,51,49,47,45)]))

Oldtown_Middle_East_Property <- data.frame(Oldtown_Middle_East_evolution_Property,Year)

Oldtown_Middle_East_map_Property <- ggplot(Oldtown_Middle_East_Property,aes(x=Year,y=Oldtown_Middle_East_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Oldtown/Middle East",x="Year",y="Property Crime")

Sandtown_Winchester_Harlem_Park_evolution_Property <- as.vector(t(Community_data[47,c(57,55,53,51,49,47,45)]))

Sandtown_Winchester_Harlem_Park_Property <- data.frame(Sandtown_Winchester_Harlem_Park_evolution_Property,Year)

Sandtown_Winchester_Harlem_Park_map_Property <- ggplot(Sandtown_Winchester_Harlem_Park_Property,aes(x=Year,y=Sandtown_Winchester_Harlem_Park_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Sandtown-Winchester/Harlem Park",x="Year",y="Property Crime")

Uptown_Druid_Heights_evolution_Property <- as.vector(t(Community_data[53,c(57,55,53,51,49,47,45)]))

Uptown_Druid_Heights_Property <- data.frame(Uptown_Druid_Heights_evolution_Property,Year)

Uptown_Druid_Heights_map_Property <- ggplot(Uptown_Druid_Heights_Property,aes(x=Year,y=Uptown_Druid_Heights_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "SUptown/Druid Heights",x="Year",y="Property Crime")

grid.arrange(Downtown_Seton_Hill_map_Property,Oldtown_Middle_East_map_Property,Sandtown_Winchester_Harlem_Park_map_Property,Uptown_Druid_Heights_map_Property,nrow=2,ncol=2,top="Four areas with HIGH property crime and HIGH CCTV density")

Property_Crime_Evolution_VS_CCTV <- Community_data[,c(1,57,47,4)] %>% 
  mutate(change_perc=((Community_data$PropertyCrimePer1000inhabitants19/Community_data$PropertyCrimePer1000inhabitants14)-1)*100)

knitr::kable(Property_Crime_Evolution_VS_CCTV[c(14,41,47,53),c(1,5)],col.names = c('Community','Property Crime per Capita % change')) %>% kable_styling(position = "center")
```
<br><br>
```{r results = 'markup'}
Washington_Village_Pigtown_evolution_Property <- as.vector(t(Community_data[54,c(57,55,53,51,49,47,45)]))

Washington_Village_Pigtown_Property <- data.frame(Washington_Village_Pigtown_evolution_Property,Year)

Washington_Village_Pigtown_map_Property <- ggplot(Washington_Village_Pigtown_Property,aes(x=Year,y=Washington_Village_Pigtown_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Washington Village/Pigtown",x="Year",y="Property Crime")

Harbor_East_Little_Italy_evolution_Property <- as.vector(t(Community_data[26,c(57,55,53,51,49,47,45)]))

Harbor_East_Little_Italy_Property <- data.frame(Harbor_East_Little_Italy_evolution_Property,Year)

Harbor_East_Little_Italy_map_Property <- ggplot(Harbor_East_Little_Italy_Property,aes(x=Year,y=Harbor_East_Little_Italy_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Harbor East/Little Italy",x="Year",y="Property Crime")

Canton_evolution_Property <- as.vector(t(Community_data[5,c(57,55,53,51,49,47,45)]))

Canton_Property <- data.frame(Canton_evolution_Property,Year)

Canton_map_Property <- ggplot(Canton_Property,aes(x=Year,y=Canton_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Canton",x="Year",y="Property Crime")

Southeastern_evolution_Property <- as.vector(t(Community_data[49,c(57,55,53,51,49,47,45)]))

Southeastern_Property <- data.frame(Southeastern_evolution_Property,Year)

Southeastern_map_Property <- ggplot(Southeastern_Property,aes(x=Year,y=Southeastern_evolution_Property)) + 
  geom_line() +
  scale_y_continuous(limits = c(0, 125), breaks =seq(0,125,25)) + 
  labs(title = "Southeastern",x="Year",y="Property Crime")

grid.arrange(Washington_Village_Pigtown_map_Property,Harbor_East_Little_Italy_map_Property,Canton_map_Property,Southeastern_map_Property,nrow=2,ncol=2,top="Four areas with HIGH property crime and LOW CCTV density")

knitr::kable(Property_Crime_Evolution_VS_CCTV[c(5,26,49,54),c(1,5)],col.names = c('Community','Property Crime per Capita % change')) %>% kable_styling(position = "center")

```

With regard to property crime, it more often increaed in areas with high CCTV density. This is despite the fact that property crime has declined city-wide. Again, these results are not statistically significant. They simply allow us to see if a trend is observable. However, when looking at the regression results between CCTV density and property crime evolution, we again find a lack of correlation confirming that CCTVs do not seem to be effective in reducing property crime. 

```{r results='markup'}

Property_Crime_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(VIO_PROP_CFS=="PROPERTY") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = str_wrap(("Overall, property crime seems to have decreased for the 2017 to 2020 period"),width=60),subtitle=str_wrap(("This explains why we should be careful when considering CCTV effectiveness in deterring property crime"),width=75),x="Year",y="Property crime occurences")

Property_Crime_Yearly_evolution_map

regression9 <- lm(Property_Crime_Evolution_VS_CCTV$change_perc~Property_Crime_Evolution_VS_CCTV$density_perc)
```
<br><br>
<div align="center">
```{r echo=FALSE, results='asis'}
stargazer(regression9,
          title = "CCTV density VS Property Crime evolution",
          type = "html",
          dep.var.labels="Property Crime per Capita % change",
          covariate.labels = c("CCTV Density","intercept"))
```
</div>
<br><br>
None of the comparisons between CCTV density and different crime type evolution seem to indicate significant relationships. Thus, it seems reasonable to conclude that in addition to being ineffective in reducing crime in general, CCTVs do not seem particularly effective in preventing any particular type of crime. However, from this analysis we found that violent crime appears to be an important determinant of CCTV density. This finding will be used to answer our fourth research question.

### 4.3 Research question 3 - Is the impact of CCTV on crime reduction higher/lower/same in higher income neighborhoods compared to lower income neighborhoods?

As the actual effectiveness of CCTV is not so clear, answering our third research question does not really make sense. Yet what we can still investigate is how crime has evolved in each area based on its poverty level. Indeed, it is interesting to see whether, for example, inequalities in terms of security between richer and poorer areas have evolved over time.

```{r results = 'markup'}

Evolution_VS_poverty <- Community_data[,c(25,15,5)] %>% 
  mutate(change=(Community_data$CrimePer1000inhabitants19/Community_data$CrimePer1000inhabitants14)-1)


ggplot(data=Evolution_VS_poverty,mapping= aes(x=change,y=hhpov19))+
  geom_point()+
  geom_smooth(method = lm,color="blue",size=0.3)+
  labs(x="Change in crime per capita between 2014 and 2019",y="% of people living below the poverty line",title = str_wrap(("Change in crime per capita and poverty do not really seem to be correlated"),width = 60),subtitle = str_wrap(("Altough the regression line might indicate a sort tendency indicating that crime might have reduced more in richer areas compared to poorer areas, the regression output below indicates a very poor correlation"),width = 70))

Evolution_VS_poverty_regr <- lm(Evolution_VS_poverty$hhpov19~Evolution_VS_poverty$change)

```

<br><br>
<div align="center">
```{r echo=FALSE, results='asis'}
stargazer(Evolution_VS_poverty_regr,
          title = "Crime evolution VS poverty level",
          type = "html",
          dep.var.labels="Poverty level",
          covariate.labels = c("Crime per Capita % change","intercept"))
```
</div>
<br><br>
The very poor $R^2$ (6.48%) indicates that there is a poor correlation between the change in crime per capita between 2014 and 2019 and the poverty metric used. Inequalities in terms of security do not seem to have evolved

### 4.4 Research question 4 - Are there more public cameras in poorer areas compared to wealthier areas?

We went to see whether there is a correlation between CCTV density and poverty level As explained in the introduction, CCTVs pose several privacy issues. One of our initial hypothesis was that the government respected more the privacy of wealthier people. So, similarly, we perform a simple linear regression. The results here are not so conclusive, since we have a poor $adjusted R^2$ (24.4%) and a poor $R^2$ (25.8%). The next sub-section illustrates this phenomenon in a map.

```{r results = 'markup'}

CCTV_VS_poverty <- CCTV_per_area %>% 
  left_join(poverty_data,by=c("Community"="CSA2010"))

regression2 <- lm(CCTV_VS_poverty$density_perc~CCTV_VS_poverty$hhpov19)
```
<br>
<div align="center">
```{r echo=FALSE, results='asis'}
stargazer(regression2,
          title = "CCTV vs poverty ",
          type = "html",
          dep.var.labels="CCTV Density",
          covariate.labels = c("Poverty level","intercept"))
```
</div>
<br>
```{r results='markup'}
ggplot(data=CCTV_VS_poverty,mapping= aes(x=hhpov19,y=density_perc)) + 
  labs(title = str_wrap(("As poverty level incrases, one tend to see subtle tendency for CCTV density to increase as well"),width = 65), x="% of people living below the poverty line",y="CCTV Density")+
  geom_point() + 
  geom_smooth(method = lm,color="blue",size=0.3)
```
<br><br>

#### 4.4.1 Mapping of CCTVs and wealth

The methodology to create the map is always the same: we ensure a perfect match, then merge the data using `left_join` and finally create the map using `tmap`. While the simple linear regression was not so conclusive, it seems like the map enables one to grasp interesting patterns and partially explain why we obtained such a poor result. First thing we see it that areas with no CCTVs often are quite wealthy (e.g. in the northern part of Baltimore). The map also enables one to see that many CCTVs are located in Downtown/Seton Hill and in Inner Harbor/Federal Hill, namely in the center of Baltimore and that the poverty level is very low in these two regions. This makes sense as centers of city are typically not a city's poorest areas. This might have contributed to the poor $R^2$ we obtained before.

```{r}

baltimore$community %in% poverty_data$CSA2010 #We see that we have a perfect match

baltimore@data <- left_join(baltimore@data, poverty_data, by = c('community' = 'CSA2010'))

```

```{r}
Wealth_and_CCTV_map <- tm_shape(baltimore)+tm_fill(col = "hhpov19", title ="% of people living below the poverty line",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)+ tm_shape(balt_dat) + tm_dots(col="black") 
```
<div align="center">
We see a high concentration of CCTVs in the centre.
```{r echo=FALSE,results='markup',dpi=72}
tmap_mode("view")
Wealth_and_CCTV_map
```
</div>
<br>

#### 4.4.2 An attempt to understand what determines CCTV density

We have seen that poverty level does not really seem to be a major determinant of CCTV density in an area. Therefore, we decided to built a multiple regression model containing various variables to investigate what could actually be the main determinant of CCTV density. This enables us to see whether city officials make decisions regarding where to implement CCTVs based on, for example, socio-economic factors, educational factors or racial factors. We retrieved six new data sets on Baltimore's open data portal. All these data sets were already tidied and constructed in the same way: they contained one observation for each area for several time periods. The first one provides information about the percent of persons between the ages of 16 and 64 who are currently unemployed. The second one provides information about the percentage of households without an internet subscription at home. Then, we retrieved some data sets about education. `HSAexam` data set provides information about the percentage of high school students who have successfully passed the H.S.A. exams while `Readiness` indicates  percentage of children whose composite score indicates full school readiness out of all kindergarten school children tested within an area in a school year. Finally, we retrieved two data sets regarding the  total number of persons that identify themselves as being racially white, respectively black or African American, out of the total number of persons living in an area. 

After importing all the data sets, we created an object called `fullmod` which is a multiple regression containing 8 independent variables to predict CCTV density: the six above-mentioned data sets, poverty level and violent crime per capita. We also create `nullmod`, this model only contain an intercept at 1. Having these two models, we performed a forward stepwise regression based on AIC criteria using  `step`. This function starts with the null model, which is technically the "worst" and "simplest" model we can imagine and adds independent variables until we are better off not adding anything (meaning: when adding a variable increase the AIC score). We then use `vif` to check whether we have a mutlicollinearity issue. This happens when one or several variable explain the same variance. A VIF score above 5 is considered severe multicollinearity. In the case at hand, two independent variables have a VIF score above 5: the two racial indicators seem to explain the same variance. By creating a simple linear regression between percentage of white people and percentage of black people, we indeed see that these two variables explain each other very well. Finally, we also tried to plot a linear regression between percentage of white people and CCTV density and saw that this really seemed to be a poor predictor of CCTV density. We therefore got rid of these two racial metrics and performed another stepwise regression. The results of this stepwise regression indicate that only violent crime, unemployment, HSA passing and poverty level should be included as independent variables and that we should not even include the rest. We have no multicollinearity this time and obtain a $R^2$ of 58.6%. Yet we also observe that out of the four partial regression coefficients, only two of them are statistically significant from zero: violent crime and unemployment. Therefore, the very last thing we did was to perform another multiple linear regression solely containing these two variables. When doing so, we obtain a satisfying $R^2$ of 53.1%, yet, unemployment in turn becomes insignificant.

_Source of the data sets:_ 

[https://arcg.is/0KOH1q] <br>
[https://arcg.is/1znCqm0] <br>
[https://arcg.is/1LiHnn0] <br>
[https://arcg.is/1nOK9X] <br>
[https://arcg.is/05LyTO] <br>
[https://arcg.is/1vqyTu0] <br>


```{r}

#Socio-economic indicators:

Unemployment <- read.csv(file = here::here("data/Unemployment_Rate.csv"))

Unemployment[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0,0,0,0,0,0,0,0)

Internet_data <- read.csv(file = here::here("data/Percent_of_Households_with_No_Internet_at_Home.csv"))

Internet_data[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0)

#Educational indicators:

HSAexam <- read.csv(file = here::here("data/Percentage_of_Students_Passing_H.S.A._Government.csv"))

HSAexam[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0,0)

Readiness <- read.csv(file = here::here("data/Kindergarten_School_Readiness.csv"))

Readiness[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0)

#Racial indicators

Caucasian_perc <- read.csv(file = here::here("data/Percent_of_Residents_-_White_Caucasian_(Non-Hispanic).csv"))

Caucasian_perc[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0,0,0,0,0)

AfroAm_perc <- read.csv(file = here::here("data/Percent_of_Residents_-_Black_African-American_(Non-Hispanic).csv"))

AfroAm_perc[56,] <- list(56,"Unassigned -- Jail",0,0,0,0,0,0,0,0,0)

Community_data <- Community_data %>% 
  left_join(HSAexam[,c(2,6)],by=c("Community"="CSA2010")) %>%
  left_join(Internet_data[,c(2,5)],by=c("Community"="CSA2010")) %>% 
  left_join(Readiness[,c(2,5)],by=c("Community"="CSA2010")) %>% 
  left_join(Unemployment[,c(2,12)],by=c("Community"="CSA2010"))%>% 
  left_join(Caucasian_perc[,c(2,9)],by=c("Community"="CSA2010"))%>% 
  left_join(AfroAm_perc[,c(2,9)],by=c("Community"="CSA2010"))
```

```{r}
fullmod <- lm(Community_data$density_perc~Community_data$ViolentCrimePerCapitaPerArea + Community_data$hhpov19 +Community_data$hsagov14 + Community_data$nohhint19+Community_data$ready13+Community_data$unempr19+Community_data$pwhite20+Community_data$paa20)

nullmod <- lm(Community_data$density_perc~1)

selAIC <- step(nullmod,scope=list(lower=nullmod,upper=fullmod),direction="forward")
#We have a satisfactory R-Squared
```
<div align="center">
```{r echo=FALSE,results='asis'}
stargazer(selAIC,
          title = "First selected model after a forward stepwise regression, 4 independent variables are retained",
          type = "html",
          dep.var.labels="CCTV Density",
          covariate.labels = c("Violent Crime (per 1000 inhabitants","HS exam passing","% of Caucasian","% of Afro-American","intercept"))
```
</div>
```{r}
library(car)
vif(selAIC) #Yet, the issue is that we have multicollinearity

lm(Community_data$paa20~Community_data$pwhite20)
summary(lm(Community_data$paa20~Community_data$pwhite20)) #This illustrates the mutlicollinearity issue, percentage of white people is highly correlated with percentage of black people

lm(Community_data$density_perc~Community_data$pwhite20+Community_data$paa20)
summary(lm(Community_data$density_perc~Community_data$pwhite20+Community_data$paa20)) #We observe that the percentage of white people is negatively correlated with CCTV density while the percentage of black people is positively correlated. However, none of the results are significant.

lm(Community_data$density_perc~Community_data$pwhite20)
summary(lm(Community_data$density_perc~Community_data$pwhite20))

lm(Community_data$density_perc~Community_data$paa20)
summary(lm(Community_data$density_perc~Community_data$paa20)) #Overall, this enables us to conclude that the race does not seem to be such a good predictor
```

```{r}
fullmod2 <- lm(Community_data$density_perc~Community_data$ViolentCrimePerCapitaPerArea + Community_data$hhpov19 +Community_data$hsagov14 + Community_data$nohhint19 + Community_data$ready13 + Community_data$unempr19)

nullmod <- lm(Community_data$density_perc~1)

selAIC2 <- step(nullmod,scope=list(lower=nullmod,upper=fullmod2),direction="forward")
summary(selAIC2) 
```
<div align="center">
```{r echo=FALSE,results='asis'}
stargazer(selAIC2,
          title = "Second selected model after a forward stepwise regression, 4 independent variables are retained",
          type = "html",
          dep.var.labels="CCTV Density",
          covariate.labels = c("Violent Crime (per 1000 inhabitants)","HS exam passing","Unemployment rate","Poverty level","intercept"))
```
</div>
```{r}
#We see that internet access information and readiness are not even included and that among the included variables, only two are significant: violent crime and unemployment rate. This enables us to conclude that like racial metrics, educational metrics are poor predictors of CCTV levels.

library(car)
vif(selAIC2) #We can try to make a multiple regression containing the only two significant variables: 

CCTV_VS_ViolentCrime_and_Unemp <- lm(Community_data$density_perc~Community_data$ViolentCrimePerCapitaPerArea+Community_data$unempr19)
```

<div align="center">
```{r echo=FALSE,results='asis'}
stargazer(CCTV_VS_ViolentCrime_and_Unemp,
          title = "Multiple regression with only unemployement and violent crime",
          type = "html",
          dep.var.labels="CCTV Density",
          covariate.labels = c("Violent Crime (per 1000 inhabitants)","Unemployment rate","intercept"))
```
</div>
<br><br>
Overall, this leads us to think that violent crime per capita in a given area is the main element that determines CCTV density. Racial metrics, educational metrics and socio-economic indicators all turned out being quite poor indicators. The results of the multiple regressions therefore allow us to conclude that the government does not seem to specifically target certain types of people and most importantly, it does not seem to specifically target least privileged society members like poorer, unemployed of less educated people.et, this statement must be mitigated. Indeed, with R-squared of approximately 50%, we are in situation where we can only explain 50% of the  variation. This means that thee approximately is 50% of the variation whose origin is unknown to us. 
