# Exploratory data analysis {.tabset}

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("scripts/setup.R"))
```

### 3.1 Calculation of the density of CCTV per community

The original CCTV data set which we observed had a slight challenge. Although it contained some neighborhood names, most of them were not matching the "standard neighborhood" names. There, to solve that we involved geospatial counting. 

Our procedure included the following steps. After reading the table and converting the data into a data table, we define what will be the coordinates of the newly created spatial file. Here we have several types of coordinates, we use X and Y which use the EPSG:3857 WGS 84 / Pseudo-Mercator coordinate system. Spatial files must have coordinate systems assigned to them. In the case at hand, we will work with the above mentioned EPSG:3857 WGS 84 / Pseudo-Mercator coordinate system for all the spatial files that we are going to use. Therefore, to ensure consistency, we create a crs object called `crs.geo1` that is going to be assigned to all the spatial files we will use. In order to assign a known crs to spatial data, we use the `proj4string` function, to which we assign `crs.geo1`.

```{r echo=TRUE}
#read in data table
balt_dat <-  fread(file = here::here("data/Baltimore_CCTV_Locations_Crime_Cameras.csv"))

#convert to data table
balt_dat <- as.data.table(balt_dat)

#make data spatial
coordinates(balt_dat) <-  c("X","Y")
crs.geo1 <-  CRS("+proj=merc +a=6378137 +b=6378137 +lat_ts=0 +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs +type=crs")
proj4string(balt_dat) <-  crs.geo1  
```

Then we plot to see the output (as cloud of points which represent all the CCTVs).

```{r}

plot(balt_dat, pch = 20, col = "steelblue") #We can use the plot function to quickly plot the SpatialPointDataFrame that we created. We see a bunch of points which represent the CCTV location in Baltimore.
```

Next, we have to work with the shapefile which is another special type of file. Basically it is a set of polygons which represent different areas of the city Baltimore. We downloaded this file on the Open Baltimore Portal. We read it in and assign this file again to our crs.geo1 coordinate system. In this way we have assured that our files have the same coordinate system.

```{r echo=TRUE}
#read in shapefile of baltimore
baltimore <-  readOGR(dsn = here::here("data/Community_Statistical_Area"), layer = "Community_Statistical_Area") #name of file and object
proj4string(baltimore) <- crs.geo1
```

We can now plot these two spatial files together to see the spread of CCTVs over the 56 community statistical areas.

```{r echo=TRUE}
#plot
plot(baltimore,main="Spread of CCTVs in different communities of Baltimore")
plot(balt_dat,pch=20, col="steelblue" , add=TRUE) #If we plot these two lines together, what we obtain is a map of baltimore, we have the 56 community statistical areas and the CCTVs on top of the map.
```

To illustrate these results numerically, we need R to count for us how many CCTV belongs to which area. Here, the function `over` counts how many CCTVs are layed over a certain polygon frame. Next, we create a new object called `counts` and  make it into a data frame (so that it is easier for us to work with it). We use  `sum` to ensure that we well and truly have 836 observations which were counted. This is the case so we are happy. Still we notice that we only have 41 rows, meaning there here are only 41 out of 56 areas where there are some CCTV. 

```{r echo=TRUE}
#Perform the count
proj4string(balt_dat)
proj4string(baltimore) #To be able to perform the count, we must ensure that the two spatial files have a similar CRS. This is the case as we attributed these two files "crs.geo1" 

res2 <- over(balt_dat,baltimore) #This function tells you to which community each CCTV belongs to
counts <- table(res2$community)
counts <- as.data.frame(counts)
colnames(counts)[1] <- "Community"
sum(counts$Freq) #We see that we have 836 observation in total, this is a good sign as our initial CCTV data set contained 836 obesrvations
```

To make that workable, we need to create a new CCTV file, from which we just add 0 to each N.A.-location. Lastly, we create a new column with the `mutate` function to calculate the CCTV-density which shows the amount of CCTV per area divided by the total amount of CCTV. 

```{r echo=TRUE}
CCTV_per_area <- area_data[2] %>% 
  left_join(counts,by="Community") #One must add the communities where there are no counts i.e no CCTV

CCTV_per_area[is.na(CCTV_per_area)] <- 0

CCTV_per_area <- mutate(CCTV_per_area, density_perc=(CCTV_per_area$Freq/(sum(CCTV_per_area$Freq)))*100)
```

#### 3.1.1 Mapping of CCTV density

We now want to map CCTV density on the Baltimore map. We first have to use the piping operator to ensure that the community that we have in the Baltimore data set are the same as the one we are having in the CCTV per are data set. As this only returns true values that means that it works and is good for further analysis. 

```{r}
library(tmap)
baltimore$community %in% CCTV_per_area$Community
```

Next, we perform a `left_join` between the Baltimore shape file and the CCTV per area data set. To hedge against the different writing styles (one time it is written with a capital letter and one time with a small letter), we use the vector in the end. Finally, we create the map with the `tmap` package. The `tmap` package somehow works as the `ggplot2` package: First, we need to define an element, it always starts with the `tm_shape` argument, and then you can add with the plus operator as many arguments as you wish. We used the Baltimore shape file, filled it with the density percentage, defined some breaks, set the borders and the finally the layout. 

```{r results='markup'}
baltimore@data <- left_join(baltimore@data, CCTV_per_area, by = c('community' = 'Community'))

CCTV_dens_map <- tm_shape(baltimore) + tm_fill(col = "density_perc", title ="CCTV density per Area in %", breaks=c(0,1,2,3,4,5,6,7,8,9,10,11)) + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

tmap_mode("plot")
CCTV_dens_map
```

### 3.2 Calculation of the crime per capita per community

What we create is the `CrimeStatsPerArea`. To achieve that we group the `crime_data_with_areas` data set by community and then use `summarize` which enables us to compute the crime frequency for each area. Then, using the population data, we can divide the crime frequency by the number of inhabitants in each area. We finally multiply this by 1000 to obtain the crime per 1000 inhabitants. Again, we added one more row in the calculations because we have no values for the prison. To make sure we made no mistake, we add up the CrimeFrequency column to see whether it equals to 349482. This is the case. We can therefore go further confidently.

```{r}
CrimeStatsPerArea <- crime_data_with_areas %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency=n())

CrimeStatsPerArea <-  mutate(CrimeStatsPerArea,CrimePer1000inhabitants=((CrimeStatsPerArea$CrimeFrequency/population_data$tpop20)*1000))

CrimeStatsPerArea <- rbind(CrimeStatsPerArea,list("Unassigned -- Jail",0,0))  #We have no information about crimes committed in jail, yet, the community statistical area encompass 56 area, including jail. In order to ensure consistency, we must add a 56th observation in this data frame.

sum(CrimeStatsPerArea$CrimeFrequency) #The total sum is 349482, which is what we expect

Community_data <- CrimeStatsPerArea[,-2] %>% 
  left_join(CCTV_per_area,by="Community") %>%
  left_join(poverty_data[,c(2,7)],by=c("Community"="CSA2010"))

```

#### 3.2.1 Mapping of crime per capita per community

We want to map  crimes per capita per community. The methodology is the same as we did for CCTV density. This time, we use the "quantile" method to create category breaks.

```{r echo=TRUE}
library(tmap)

baltimore$community %in% CrimeStatsPerArea$Community #We see that we have a perfect match

baltimore@data <- left_join(baltimore@data, CrimeStatsPerArea, by = c('community' = 'Community'))

Crime_per_capita_map <- tm_shape(baltimore) + tm_fill(col = "CrimePer1000inhabitants", title ="Crime per capita",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

tmap_mode("plot")
Crime_per_capita_map
```

#### 3.2.2 Creation of a distorted map

To observe crime per capita per community repartition in Baltimore visually, we decided to use a distorted map. Again, we use the `tmap` package together with the `cartogram_ncont` function which basically distort the map based on intensity of crime per capita in each community. Concretely, we want to show that the crime per capita is higher in the city center, compared to the suburban areas. This can be shown quite neatly graphically. 

```{r}

Distorted_Crime_map <- tm_shape(cartogram_ncont(baltimore, "CrimePer1000inhabitants"))+tm_fill(col = "CrimePer1000inhabitants", title ="Crime per capita per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.07) #This map distorts the size of each area depending on their respective crime per capita It is interesting as it enables one to see that higher crime per capita tends to be concentrated in the city center.

tmap_mode("plot")
Distorted_Crime_map
```

#### 3.2.3 The prison anomaly

One may wonder what this little square with no crime per capita, surrounded by CCTVs in the very center of Baltimore is. It actually is the prison. Zooming on this little square is interesting. In order to create a "sub-map", we create a smaller area using the `st-bbox` function. The values indicated in the function represent the most extreme values on the x-axis and y-axis of a map using the EPSG:3857 WGS 84 / Pseudo-Mercator coordinate system. Then, using `tm_shape` with the new spatial file called `Prison_map`as argument, we create a map in the same way as we have done before. As we want to be able to locate this smaller area in the picture map of Baltimore, we must also create a Baltimore map with a rectangle representing the newly created "sub-area". In order to combine these two maps together, we run the two last lines together and use the `viewport` function. The output is a zoom on the desired area combined with the bigger map having a rectangle over the area which we are looking at and analyzing. The reason why we see so many CCTVs located on the right-hand side of the map is that the main entrance is located there.

```{r}
tmap_mode("plot")

Prison_area <-  st_bbox(c(xmin = -8529169.92, xmax = -8526465.97,
                      ymin =4764196.55, ymax = 4765056.50),
                    crs = st_crs(baltimore)) %>% st_as_sfc()
 
Prison_map <- tm_shape(Prison_area) + tm_borders(col="black",alpha=0.3)+ tm_shape(baltimore) + tm_fill(col = "CrimePer1000inhabitants", title ="Crime per capita per Area",style = "quantile") + tm_borders(col="black") + tm_layout(inner.margins = 0.05,frame.lwd = 5,title = "Zoom on Baltimore Prison",title.position = c('left', 'top'))+tm_scale_bar(position = c("left", "top"))+ tm_shape(balt_dat) + tm_dots(col="black") #This map zooms on the prison. This "Area" is special. We have no data on crime there, we can also see that the there is a huge concentration of CCTVs directly next to the prison.


Baltimore_map <- tm_shape(baltimore) + tm_borders()+ tm_shape(Prison_area) + tm_borders(lwd = 3,col = "red") + tm_layout(frame.lwd = 6,inner.margins = 0.05)


Prison_map
print(Baltimore_map, vp = viewport(0.8, 0.27, width = 0.5, height = 0.5)) #By running these two lines together, we obtain 
```
### 3.3 Calculation of crime per capita by type of crime

#### 3.3.1 Felonies and Misdemeanors

First thing we do here is to compute the unique values of the description column of the crime data set. We see that we have 14 types of crime. We want to observe crimes by types, therefore we want to make new classifications. The law consists of three basic classifications of criminal offenses including **infractions**, **misdemeanors**, and **felonies**. 
In our data set, we have no infractions. The 14 types of crime are divided in this way into the two remaining categories.

  + **Misdemeanor:** LARCENY FROM AUTO,COMMON ASSAULT, ROBBERY - COMMERCIAL, LARCENY
  + **Felony:** RAPE, ARSON, HOMICIDE, BURGLARY, AUTO THEFT, ROBBERY - CARJACKING, AGG. ASSAULT, ROBBERY - STREET, ROBBERY - RESIDENCE, SHOOTING
  
```{r}
unique(crime_data_with_areas$Description)

#We see that we have 14 types of crime. We want to observe crimes by types, therefore we want to make new classifications.The law consists of three basic classifications of criminal offenses including infractions, misdemeanors, and felonies. In our data set, we have infractions.

#Misdemeanor:LARCENY FROM AUTO,COMMON ASSAULT, ROBBERY - COMMERCIAL, LARCENY
#Felony: RAPE, ARSON, HOMICIDE, BURGLARY, AUTO THEFT, ROBBERY - CARJACKING, AGG. ASSAULT, ROBBERY - STREET, ROBBERY - RESIDENCE, SHOOTING
```

Next we create a data set which is called crime_cat and basically tells you which recorded crime type belongs to which crime category. This data set will be used later to make a left joint with the crime_data_per_area. Finally, we are left with the crime data sets with the area datas et with a new column which concerns whether the crime was a felony or a misdemeanor. 

```{r}
crime_cat <- data.frame(Category=c("Misdemeanor","Felony"), Description=c(c("LARCENY FROM AUTO,COMMON ASSAULT,ROBBERY - COMMERCIAL,LARCENY"),c("RAPE,ARSON,HOMICIDE,BURGLARY,AUTO THEFT,ROBBERY - CARJACKING,AGG. ASSAULT,ROBBERY - STREET,ROBBERY - RESIDENCE,SHOOTING")))

crime_cat <- separate_rows(crime_cat, Description, sep = ",")

crime_cat$Description %in% unique(crime_data_with_areas$Description) #Ensure we have a perfect match

crime_data_with_areas <- crime_data_with_areas %>% 
  left_join(crime_cat,by="Description") #We had a new variable to our crime data set
```

Next, we compute the Crime_PerCategory_PerArea. Here we use the piping operator and this time we group by the community and category and obtain the results. Again, we check that we indeed have 349482 observations. Moreover, from that we compute both felony and misdemeanors per capita in each community and (again) add the prison line into the newly created data sets.  

```{r echo=TRUE}
CrimePerCategoryPerArea <- crime_data_with_areas %>% 
  group_by(Community,Category) %>%
  summarize(RepartitionPerCategoryPerArea=n())

sum(CrimePerCategoryPerArea$RepartitionPerCategoryPerArea) #Again, we check that we indeed have 349482 observations

CrimeCategoryRepartition <- CrimePerCategoryPerArea %>% 
  group_by(Category) %>% 
  summarise(Repartition=sum(RepartitionPerCategoryPerArea)) #We observe that in Baltimore, the number of felony is close to the number of misdemeanor

FelonyStats <-  CrimePerCategoryPerArea %>% filter(Category=="Felony") 

FelonyStats$FelonyPerCapitaPerArea <-((CrimePerCategoryPerArea%>% filter(Category=="Felony"))[[3]]/population_data$tpop20)*1000

FelonyStats[56,] <- list("Unassigned -- Jail","Felony",0,0)

MisdemeanorStats <-  CrimePerCategoryPerArea %>% filter(Category=="Misdemeanor") 

MisdemeanorStats$MisdemeanorPerCapitaPerArea <-((CrimePerCategoryPerArea%>% filter(Category=="Misdemeanor"))[[3]]/population_data$tpop20)*1000

MisdemeanorStats[56,] <- list("Unassigned -- Jail","Misdemeanor",0,0)

Community_data <- Community_data %>% 
  left_join(FelonyStats[,-c(2:3)],by="Community") %>%
  left_join(MisdemeanorStats[,-c(2:3)],by="Community")

```

#### 3.3.2 Mapping of felonies and Misdemeanors

After ensuring that we have a perfect match we perform a left joint for felony and misdemeanor and map everything. 

```{r echo=TRUE}

#Felony

baltimore$community %in% FelonyStats$Community

baltimore@data <- left_join(baltimore@data, FelonyStats, by = c('community' = 'Community'))

Felony_map <- tm_shape(baltimore) + tm_fill(col = "FelonyPerCapitaPerArea", title ="Felony per capita per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

Felony_map

#Misdemeanor

baltimore$community %in% MisdemeanorStats$Community

baltimore@data <- left_join(baltimore@data, MisdemeanorStats, by = c('community' = 'Community'))

Misdemeanor_map <- tm_shape(baltimore) + tm_fill(col = "MisdemeanorPerCapitaPerArea", title ="Misdemeanor per capita per Area in %",style = "quantile") + tm_borders(col="black",alpha=0.3) + tm_layout(inner.margins = 0.05)

Misdemeanor_map

```

#### 3.3.3 Felonies VS Misdemeanors - Do we have an equal crime type distribution?

It is always interesting to see whether we can spot patterns in crime date. The idea here is to analyse whether  we tend to observe an equal distribution of felony and misdemeanors in each area. By computing a simple linear regression, we see that the two types of crime seems rather equally distributed in each area. Still, it is interesting to observe that the biggest outline on the scatter plot is Downtown/Seton Hill. In Downtown, misdemeanor per capita is much larger than the felony per capita We don't whether this finding is relevant, yet, it must be mentioned that this area also is one of the richest area in Baltimore. This might **suggest** the idea that richer areas are more impacted by less severe crimes.

```{r echo=FALSE, results = 'markup'}

Felony_VS_Misdemeanor <- FelonyStats %>% 
  left_join(MisdemeanorStats,by="Community")

regression4 <- lm(Felony_VS_Misdemeanor$FelonyPerCapitaPerArea~Felony_VS_Misdemeanor$MisdemeanorPerCapitaPerArea)
#This allows us to see whether Felony and Misdemeanors are correlated. This seems to be the case

stargazer(regression4,
          title = "Felony vs Misdemeanor",
          type = "text")

ggplot(data=Felony_VS_Misdemeanor,mapping= aes(x=FelonyPerCapitaPerArea,y=MisdemeanorPerCapitaPerArea)) + 
  labs(title = "Misdemeanor VS Felony", x="Felons per capita",y="Misdemeanor per capita")+
  geom_point(shape=1) + 
  geom_smooth(method = lm,color="blue",size=0.3)

#Still, we see that there seems ot be some outliers. I don't know if it is relevant but the biggest outlier is Downtown/Seton Hill, is turns out it also is one of the richest area in Baltimore.
```


#### 3.3.4 Violent crime and Property crime

As mentioned earlier, it is also possible to divide the crimes committed in Baltimore by 'type' of crime. A distinction is generally made between property crime and violent crime. In a property crime, a victim's property is stolen or destroyed, without the use or threat of force against the victim. Property crimes include burglary and theft as well as vandalism and arson. In a violent crime, a victim is harmed by or threatened with violence. Violent crimes include rape and sexual assault, robbery, assault and murder.

In order determine whether the crimes contained in our `crime_data_with_area`. We will use a data set once again provided by the Baltimore open data portal. This data set provides information about the crime codes used by the police to categorize crimes. We first import the data set. Then, we compare whether codes are well and truly similar, three crime codes are written with an extra blank space afterward. We correct that. Then, suing the `left_join` function, we add a new column to our `crime_data_with_area` data frame. We then wish to create data frames for both violent and property crime. The methodology is the same as we used for felonies and misdemeanors.

```{r echo=TRUE}

crimecode_data <- read.csv(file = here::here("data/Balt_CRIME_CODES.csv"))

unique(crime_data_with_areas$CrimeCode) %in% unique(crimecode_data$CODE) #We identify spelling errors

crimecode_data$CODE[185] <- "8H"
crimecode_data$CODE[186] <- "8I"
crimecode_data$CODE[187] <- "8J"

crime_data_with_areas <- crime_data_with_areas %>% 
  left_join(crimecode_data[,c(1,8)],by=c("CrimeCode"="CODE"))

unique(crime_data_with_areas$VIO_PROP_CFS)
which(is.na(crime_data_with_areas$VIO_PROP_CFS)) #We ensure that we have no NAs

CrimePerCategory2PerArea <- crime_data_with_areas %>% 
  group_by(Community,VIO_PROP_CFS) %>%
  summarize(RepartitionPerCategory2PerArea=n())

sum(CrimePerCategory2PerArea$RepartitionPerCategory2PerArea) #Again, we check that we indeed have 349482 observations

CrimeCategory2Repartition <- CrimePerCategory2PerArea %>% 
  group_by(VIO_PROP_CFS) %>% 
  summarise(Repartition=sum(RepartitionPerCategory2PerArea))

PropertyStats <-  CrimePerCategory2PerArea %>% filter(VIO_PROP_CFS=="PROPERTY") 

PropertyStats$PropertyCrimePerCapitaPerArea <-((CrimePerCategory2PerArea%>% filter(VIO_PROP_CFS=="PROPERTY"))[[3]]/population_data$tpop20)*1000

PropertyStats[56,] <- list("Unassigned -- Jail","PROPERTY",0,0)

ViolentStats <-  CrimePerCategory2PerArea %>% filter(VIO_PROP_CFS=="VIOLENT") 

ViolentStats$ViolentCrimePerCapitaPerArea <-((CrimePerCategory2PerArea%>% filter(VIO_PROP_CFS=="VIOLENT"))[[3]]/population_data$tpop20)*1000

ViolentStats[56,] <- list("Unassigned -- Jail","PROPERTY",0,0)

Community_data <- Community_data %>% 
  left_join(ViolentStats[,c(1,4)],by="Community") %>% 
  left_join(PropertyStats[,c(1,4)],by="Community")

```

### 3.4 Calculation of crime evolution

The idea is that we want to get information about how crime evolved. Here we could have done a loop, but could not yet find a way to properly do it. We have created a data set for each year.
The results are interesting. If we compare how many observations we have in each crime-per year data sets, we see that we have ~40.000ish cases a year except from 2020 (which is due to COVID) and the year 2021 (which is not finished. We don't make any datasets for the year 2013 and below, because we see that we have not many observations which date prior to the year 2013.
The graph represent the monthly evolution of crime for each year. We see that there seems to be a sort of pattern and that, each year, crime increases mid-year before decreasing in December.

```{r echo=TRUE}

Crime_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31"))

Crime_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31"))

Crime_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31"))

Crime_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31"))

Crime_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31"))

Crime_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31"))

Crime_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31"))

Crime_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31"))

crime_data_with_areas %>%  filter(CrimeDateTime < as.Date("2014-01-01")) #We see that we have very few (76) observations before 2014, thus we do not consider them

Crime_Monthly_evolution_map <- crime_data_with_areas %>% 
  count(month=floor_date(CrimeDateTime,"month")) %>% 
  ggplot(aes(month,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2021-08-31"))) #This enables us to see how crime evolve, month after month

Crime_Monthly_evolution_map
```

Next, we calculate the crime per capita for each year with the piping operator, grouping by community and summarize the rates. In the end we create the crime evolution data sets which is a combination of all the data. 

```{r echo=TRUE}
#_____ Calculations of the crime rates

CrimePerCapitaPerArea2021 <- Crime_in_2021 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency21=n())

CrimePerCapitaPerArea2021 <-  mutate(CrimePerCapitaPerArea2021,CrimePer1000inhabitants21=((CrimePerCapitaPerArea2021$CrimeFrequency21/population_data$tpop20)*1000))

CrimePerCapitaPerArea2021 <- rbind(CrimePerCapitaPerArea2021,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2020 <- Crime_in_2020 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency20=n())

CrimePerCapitaPerArea2020 <-  mutate(CrimePerCapitaPerArea2020,CrimePer1000inhabitants20=((CrimePerCapitaPerArea2020$CrimeFrequency20/population_data$tpop20)*1000))

CrimePerCapitaPerArea2020 <- rbind(CrimePerCapitaPerArea2020,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2019 <- Crime_in_2019 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency19=n())

CrimePerCapitaPerArea2019 <-  mutate(CrimePerCapitaPerArea2019,CrimePer1000inhabitants19=((CrimePerCapitaPerArea2019$CrimeFrequency19/population_data$tpop20)*1000))

CrimePerCapitaPerArea2019 <- rbind(CrimePerCapitaPerArea2019,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2018 <- Crime_in_2018 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency18=n())

CrimePerCapitaPerArea2018 <-  mutate(CrimePerCapitaPerArea2018,CrimePer1000inhabitants18=((CrimePerCapitaPerArea2018$CrimeFrequency18/population_data$tpop20)*1000))

CrimePerCapitaPerArea2018 <- rbind(CrimePerCapitaPerArea2018,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2017 <- Crime_in_2017 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency17=n())

CrimePerCapitaPerArea2017 <-  mutate(CrimePerCapitaPerArea2017,CrimePer1000inhabitants17=((CrimePerCapitaPerArea2017$CrimeFrequency17/population_data$tpop20)*1000))

CrimePerCapitaPerArea2017 <- rbind(CrimePerCapitaPerArea2017,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2016 <- Crime_in_2016 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency16=n())

CrimePerCapitaPerArea2016 <-  mutate(CrimePerCapitaPerArea2016,CrimePer1000inhabitants16=((CrimePerCapitaPerArea2016$CrimeFrequency16/population_data$tpop20)*1000))

CrimePerCapitaPerArea2016 <- rbind(CrimePerCapitaPerArea2016,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2015 <- Crime_in_2015 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency15=n())

CrimePerCapitaPerArea2015 <-  mutate(CrimePerCapitaPerArea2015,CrimePer1000inhabitants15=((CrimePerCapitaPerArea2015$CrimeFrequency15/population_data$tpop20)*1000))

CrimePerCapitaPerArea2015 <- rbind(CrimePerCapitaPerArea2015,list("Unassigned -- Jail",0,0))

CrimePerCapitaPerArea2014 <- Crime_in_2014 %>% 
  group_by(Community) %>%
  summarize(CrimeFrequency14=n())

CrimePerCapitaPerArea2014 <-  mutate(CrimePerCapitaPerArea2014,CrimePer1000inhabitants14=((CrimePerCapitaPerArea2014$CrimeFrequency14/population_data$tpop20)*1000))

CrimePerCapitaPerArea2014 <- rbind(CrimePerCapitaPerArea2014,list("Unassigned -- Jail",0,0))

crime_evolution <- CrimePerCapitaPerArea2021 %>% 
  left_join(CrimePerCapitaPerArea2020,by="Community") %>% 
  left_join(CrimePerCapitaPerArea2019,by="Community") %>%
  left_join(CrimePerCapitaPerArea2018,by="Community") %>%
  left_join(CrimePerCapitaPerArea2017,by="Community") %>% 
  left_join(CrimePerCapitaPerArea2016,by="Community") %>% 
  left_join(CrimePerCapitaPerArea2015,by="Community") %>% 
  left_join(CrimePerCapitaPerArea2014,by="Community")

Community_data <- Community_data %>% 
  left_join(crime_evolution,by="Community")

```

Another interesting way to visualise how crime evolved is by using an animated map. We can create animated maps using the `tmap_animation` function. Yet, in order to be in position to use it, we have to create a very particular tibble. In the case at hand, we want our animated map to display crime per capita evolution over 7 years (from 2014 to 2020, we get ride of 2021 as the year is not complete). Therefore, we must have 7 x 56 observations, one crime per capita value for each year, for each 56 area. Yet, the tibble becomes a bit more peculiar as for each observation, we have to add a in a separate column, a polygon (which is an S4 element) corresponding to the area in question. It is not possible to use a function like the `rep` function to replicate S4 elements, therefore, we had to do that manually.

Once the tibble is built, we want to merge the data contained in it in a SpatialPolygonsDataFrame. We want to use the `baltimore` SpatialPolygonsDataFrame.However, as the tibble contains 392 observations, this will enlarge our our SpatialPolygonsDataFrame. As the `baltimore` object is also used for other purposes, we create an alias. Then, we merge the newly created tibble with the newly created alias, simply using `left_join`. We create the `bbox` object as well as an object called `pb`. The first element allows us to delimit the geographical area of interest and the second allows us to create custom classes. Finally, we crate a map using the `tm_shape` function. We animate the latter using `tmap_animation`.

```{r echo=TRUE}

anim_tibble <-  tibble(Year=rep(2020:2014,56),Community=rep(Community_data$Community,each=7),CrimeRate=as.vector(t(crime_evolution[,-c(1,2,3,4,6,8,10,12,14,16)])),geometry=list(
  baltimore@polygons[[1]],baltimore@polygons[[1]],baltimore@polygons[[1]],baltimore@polygons[[1]],baltimore@polygons[[1]],baltimore@polygons[[1]],baltimore@polygons[[1]],
  baltimore@polygons[[2]],baltimore@polygons[[2]],baltimore@polygons[[2]],baltimore@polygons[[2]],baltimore@polygons[[2]],baltimore@polygons[[2]],baltimore@polygons[[2]],
  baltimore@polygons[[3]],baltimore@polygons[[3]],baltimore@polygons[[3]],baltimore@polygons[[3]],baltimore@polygons[[3]],baltimore@polygons[[3]],baltimore@polygons[[3]],
  baltimore@polygons[[4]],baltimore@polygons[[4]],baltimore@polygons[[4]],baltimore@polygons[[4]],baltimore@polygons[[4]],baltimore@polygons[[4]],baltimore@polygons[[4]],
  baltimore@polygons[[5]],baltimore@polygons[[5]],baltimore@polygons[[5]],baltimore@polygons[[5]],baltimore@polygons[[5]],baltimore@polygons[[5]],baltimore@polygons[[5]],
  baltimore@polygons[[6]],baltimore@polygons[[6]],baltimore@polygons[[6]],baltimore@polygons[[6]],baltimore@polygons[[6]],baltimore@polygons[[6]],baltimore@polygons[[6]],
  baltimore@polygons[[7]],baltimore@polygons[[7]],baltimore@polygons[[7]],baltimore@polygons[[7]],baltimore@polygons[[7]],baltimore@polygons[[7]],baltimore@polygons[[7]],
  baltimore@polygons[[8]],baltimore@polygons[[8]],baltimore@polygons[[8]],baltimore@polygons[[8]],baltimore@polygons[[8]],baltimore@polygons[[8]],baltimore@polygons[[8]],
  baltimore@polygons[[9]],baltimore@polygons[[9]],baltimore@polygons[[9]],baltimore@polygons[[9]],baltimore@polygons[[9]],baltimore@polygons[[9]],baltimore@polygons[[9]],
  baltimore@polygons[[10]],baltimore@polygons[[10]],baltimore@polygons[[10]],baltimore@polygons[[10]],baltimore@polygons[[10]],baltimore@polygons[[10]],baltimore@polygons[[10]],
  baltimore@polygons[[11]],baltimore@polygons[[11]],baltimore@polygons[[11]],baltimore@polygons[[11]],baltimore@polygons[[11]],baltimore@polygons[[11]],baltimore@polygons[[11]],
  baltimore@polygons[[12]],baltimore@polygons[[12]],baltimore@polygons[[12]],baltimore@polygons[[12]],baltimore@polygons[[12]],baltimore@polygons[[12]],baltimore@polygons[[12]],
  baltimore@polygons[[13]],baltimore@polygons[[13]],baltimore@polygons[[13]],baltimore@polygons[[13]],baltimore@polygons[[13]],baltimore@polygons[[13]],baltimore@polygons[[13]],
  baltimore@polygons[[14]],baltimore@polygons[[14]],baltimore@polygons[[14]],baltimore@polygons[[14]],baltimore@polygons[[14]],baltimore@polygons[[14]],baltimore@polygons[[14]],
  baltimore@polygons[[15]],baltimore@polygons[[15]],baltimore@polygons[[15]],baltimore@polygons[[15]],baltimore@polygons[[15]],baltimore@polygons[[15]],baltimore@polygons[[15]],
  baltimore@polygons[[16]],baltimore@polygons[[16]],baltimore@polygons[[16]],baltimore@polygons[[16]],baltimore@polygons[[16]],baltimore@polygons[[16]],baltimore@polygons[[16]],
  baltimore@polygons[[17]],baltimore@polygons[[17]],baltimore@polygons[[17]],baltimore@polygons[[17]],baltimore@polygons[[17]],baltimore@polygons[[17]],baltimore@polygons[[17]],
  baltimore@polygons[[18]],baltimore@polygons[[18]],baltimore@polygons[[18]],baltimore@polygons[[18]],baltimore@polygons[[18]],baltimore@polygons[[18]],baltimore@polygons[[18]],
  baltimore@polygons[[19]],baltimore@polygons[[19]],baltimore@polygons[[19]],baltimore@polygons[[19]],baltimore@polygons[[19]],baltimore@polygons[[19]],baltimore@polygons[[19]],
  baltimore@polygons[[20]],baltimore@polygons[[20]],baltimore@polygons[[20]],baltimore@polygons[[20]],baltimore@polygons[[20]],baltimore@polygons[[20]],baltimore@polygons[[20]],
  baltimore@polygons[[21]],baltimore@polygons[[21]],baltimore@polygons[[21]],baltimore@polygons[[21]],baltimore@polygons[[21]],baltimore@polygons[[21]],baltimore@polygons[[21]],
  baltimore@polygons[[22]],baltimore@polygons[[22]],baltimore@polygons[[22]],baltimore@polygons[[22]],baltimore@polygons[[22]],baltimore@polygons[[22]],baltimore@polygons[[22]],
  baltimore@polygons[[23]],baltimore@polygons[[23]],baltimore@polygons[[23]],baltimore@polygons[[23]],baltimore@polygons[[23]],baltimore@polygons[[23]],baltimore@polygons[[23]],
  baltimore@polygons[[24]],baltimore@polygons[[24]],baltimore@polygons[[24]],baltimore@polygons[[24]],baltimore@polygons[[24]],baltimore@polygons[[24]],baltimore@polygons[[24]],
  baltimore@polygons[[25]],baltimore@polygons[[25]],baltimore@polygons[[25]],baltimore@polygons[[25]],baltimore@polygons[[25]],baltimore@polygons[[25]],baltimore@polygons[[25]],
  baltimore@polygons[[26]],baltimore@polygons[[26]],baltimore@polygons[[26]],baltimore@polygons[[26]],baltimore@polygons[[26]],baltimore@polygons[[26]],baltimore@polygons[[26]],
  baltimore@polygons[[27]],baltimore@polygons[[27]],baltimore@polygons[[27]],baltimore@polygons[[27]],baltimore@polygons[[27]],baltimore@polygons[[27]],baltimore@polygons[[27]],
  baltimore@polygons[[28]],baltimore@polygons[[28]],baltimore@polygons[[28]],baltimore@polygons[[28]],baltimore@polygons[[28]],baltimore@polygons[[28]],baltimore@polygons[[28]],
  baltimore@polygons[[29]],baltimore@polygons[[29]],baltimore@polygons[[29]],baltimore@polygons[[29]],baltimore@polygons[[29]],baltimore@polygons[[29]],baltimore@polygons[[29]],
  baltimore@polygons[[30]],baltimore@polygons[[30]],baltimore@polygons[[30]],baltimore@polygons[[30]],baltimore@polygons[[30]],baltimore@polygons[[30]],baltimore@polygons[[30]],
  baltimore@polygons[[31]],baltimore@polygons[[31]],baltimore@polygons[[31]],baltimore@polygons[[31]],baltimore@polygons[[31]],baltimore@polygons[[31]],baltimore@polygons[[31]],
  baltimore@polygons[[32]],baltimore@polygons[[32]],baltimore@polygons[[32]],baltimore@polygons[[32]],baltimore@polygons[[32]],baltimore@polygons[[32]],baltimore@polygons[[32]],
  baltimore@polygons[[33]],baltimore@polygons[[33]],baltimore@polygons[[33]],baltimore@polygons[[33]],baltimore@polygons[[33]],baltimore@polygons[[33]],baltimore@polygons[[33]],
  baltimore@polygons[[34]],baltimore@polygons[[34]],baltimore@polygons[[34]],baltimore@polygons[[34]],baltimore@polygons[[34]],baltimore@polygons[[34]],baltimore@polygons[[34]],
  baltimore@polygons[[35]],baltimore@polygons[[35]],baltimore@polygons[[35]],baltimore@polygons[[35]],baltimore@polygons[[35]],baltimore@polygons[[35]],baltimore@polygons[[35]],
  baltimore@polygons[[36]],baltimore@polygons[[36]],baltimore@polygons[[36]],baltimore@polygons[[36]],baltimore@polygons[[36]],baltimore@polygons[[36]],baltimore@polygons[[36]],
  baltimore@polygons[[37]],baltimore@polygons[[37]],baltimore@polygons[[37]],baltimore@polygons[[37]],baltimore@polygons[[37]],baltimore@polygons[[37]],baltimore@polygons[[37]],
  baltimore@polygons[[38]],baltimore@polygons[[38]],baltimore@polygons[[38]],baltimore@polygons[[38]],baltimore@polygons[[38]],baltimore@polygons[[38]],baltimore@polygons[[38]],
  baltimore@polygons[[39]],baltimore@polygons[[39]],baltimore@polygons[[39]],baltimore@polygons[[39]],baltimore@polygons[[39]],baltimore@polygons[[39]],baltimore@polygons[[39]],
  baltimore@polygons[[40]],baltimore@polygons[[40]],baltimore@polygons[[40]],baltimore@polygons[[40]],baltimore@polygons[[40]],baltimore@polygons[[40]],baltimore@polygons[[40]],
  baltimore@polygons[[41]],baltimore@polygons[[41]],baltimore@polygons[[41]],baltimore@polygons[[41]],baltimore@polygons[[41]],baltimore@polygons[[41]],baltimore@polygons[[41]],
  baltimore@polygons[[42]],baltimore@polygons[[42]],baltimore@polygons[[42]],baltimore@polygons[[42]],baltimore@polygons[[42]],baltimore@polygons[[42]],baltimore@polygons[[42]],
  baltimore@polygons[[43]],baltimore@polygons[[43]],baltimore@polygons[[43]],baltimore@polygons[[43]],baltimore@polygons[[43]],baltimore@polygons[[43]],baltimore@polygons[[43]],
  baltimore@polygons[[44]],baltimore@polygons[[44]],baltimore@polygons[[44]],baltimore@polygons[[44]],baltimore@polygons[[44]],baltimore@polygons[[44]],baltimore@polygons[[44]],
  baltimore@polygons[[45]],baltimore@polygons[[45]],baltimore@polygons[[45]],baltimore@polygons[[45]],baltimore@polygons[[45]],baltimore@polygons[[45]],baltimore@polygons[[45]],
  baltimore@polygons[[46]],baltimore@polygons[[46]],baltimore@polygons[[46]],baltimore@polygons[[46]],baltimore@polygons[[46]],baltimore@polygons[[46]],baltimore@polygons[[46]],
  baltimore@polygons[[47]],baltimore@polygons[[47]],baltimore@polygons[[47]],baltimore@polygons[[47]],baltimore@polygons[[47]],baltimore@polygons[[47]],baltimore@polygons[[47]],
  baltimore@polygons[[48]],baltimore@polygons[[48]],baltimore@polygons[[48]],baltimore@polygons[[48]],baltimore@polygons[[48]],baltimore@polygons[[48]],baltimore@polygons[[48]],
  baltimore@polygons[[49]],baltimore@polygons[[49]],baltimore@polygons[[49]],baltimore@polygons[[49]],baltimore@polygons[[49]],baltimore@polygons[[49]],baltimore@polygons[[49]],
  baltimore@polygons[[50]],baltimore@polygons[[50]],baltimore@polygons[[50]],baltimore@polygons[[50]],baltimore@polygons[[50]],baltimore@polygons[[50]],baltimore@polygons[[50]],
  baltimore@polygons[[51]],baltimore@polygons[[51]],baltimore@polygons[[51]],baltimore@polygons[[51]],baltimore@polygons[[51]],baltimore@polygons[[51]],baltimore@polygons[[51]],
  baltimore@polygons[[52]],baltimore@polygons[[52]],baltimore@polygons[[52]],baltimore@polygons[[52]],baltimore@polygons[[52]],baltimore@polygons[[52]],baltimore@polygons[[52]],
  baltimore@polygons[[53]],baltimore@polygons[[53]],baltimore@polygons[[53]],baltimore@polygons[[53]],baltimore@polygons[[53]],baltimore@polygons[[53]],baltimore@polygons[[53]],
  baltimore@polygons[[54]],baltimore@polygons[[54]],baltimore@polygons[[54]],baltimore@polygons[[54]],baltimore@polygons[[54]],baltimore@polygons[[54]],baltimore@polygons[[54]],
  baltimore@polygons[[55]],baltimore@polygons[[55]],baltimore@polygons[[55]],baltimore@polygons[[55]],baltimore@polygons[[55]],baltimore@polygons[[55]],baltimore@polygons[[55]],
  baltimore@polygons[[56]],baltimore@polygons[[56]],baltimore@polygons[[56]],baltimore@polygons[[56]],baltimore@polygons[[56]],baltimore@polygons[[56]],baltimore@polygons[[56]]))

baltimore_alias <- baltimore

baltimore_alias@polygons <- anim_tibble$geometry

baltimore_alias@data$community %in% anim_tibble$Community #Again, we ensure that we have a perfect match

baltimore_alias@data <-left_join(baltimore_alias@data,anim_tibble,by = c('community' = 'Community'))

bbox <- baltimore@bbox
pb <-  c(0,25,50,75,100,125,150,175,200,225,250)

animated_crime_map <- tm_shape(baltimore_alias,bbox = bbox, projection = crs.geo1) +
  tm_polygons("CrimeRate",breaks=pb) +
  tm_facets(free.scales.fill = F,along = "Year")+tm_shape(baltimore)+tm_borders()

tmap_animation(animated_crime_map, delay=100)

#maybe write.gif

```

###3.4.1 Calculation of violent crime and property crime evolution

We can make the exact same computation to calculate violent crime and property crime evolution.

```{r echo=TRUE}

Violent_Crime_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

Violent_Crime_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31")) %>% filter(VIO_PROP_CFS=="VIOLENT")

ViolentCrimePerCapitaPerArea2021 <- Violent_Crime_in_2021 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency21=n())

ViolentCrimePerCapitaPerArea2021 <-  mutate(ViolentCrimePerCapitaPerArea2021,ViolentCrimePer1000inhabitants21=((ViolentCrimePerCapitaPerArea2021$ViolentCrimeFrequency21/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2021 <- rbind(ViolentCrimePerCapitaPerArea2021,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2020 <- Violent_Crime_in_2020 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency20=n())

ViolentCrimePerCapitaPerArea2020 <-  mutate(ViolentCrimePerCapitaPerArea2020,ViolentCrimePer1000inhabitants20=((ViolentCrimePerCapitaPerArea2020$ViolentCrimeFrequency20/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2020 <- rbind(ViolentCrimePerCapitaPerArea2020,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2019 <- Violent_Crime_in_2019 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency19=n())

ViolentCrimePerCapitaPerArea2019 <-  mutate(ViolentCrimePerCapitaPerArea2019,ViolentCrimePer1000inhabitants19=((ViolentCrimePerCapitaPerArea2019$ViolentCrimeFrequency19/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2019 <- rbind(ViolentCrimePerCapitaPerArea2019,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2018 <- Violent_Crime_in_2018 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency18=n())

ViolentCrimePerCapitaPerArea2018 <-  mutate(ViolentCrimePerCapitaPerArea2018,ViolentCrimePer1000inhabitants18=((ViolentCrimePerCapitaPerArea2018$ViolentCrimeFrequency18/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2018 <- rbind(ViolentCrimePerCapitaPerArea2018,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2017 <- Violent_Crime_in_2017 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency17=n())

ViolentCrimePerCapitaPerArea2017 <-  mutate(ViolentCrimePerCapitaPerArea2017,ViolentCrimePer1000inhabitants17=((ViolentCrimePerCapitaPerArea2017$ViolentCrimeFrequency17/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2017 <- rbind(ViolentCrimePerCapitaPerArea2017,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2016 <- Violent_Crime_in_2016 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency16=n())

ViolentCrimePerCapitaPerArea2016 <-  mutate(ViolentCrimePerCapitaPerArea2016,ViolentCrimePer1000inhabitants16=((ViolentCrimePerCapitaPerArea2016$ViolentCrimeFrequency16/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2016 <- rbind(ViolentCrimePerCapitaPerArea2016,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2015 <- Violent_Crime_in_2015 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency15=n())

ViolentCrimePerCapitaPerArea2015 <-  mutate(ViolentCrimePerCapitaPerArea2015,ViolentCrimePer1000inhabitants15=((ViolentCrimePerCapitaPerArea2015$ViolentCrimeFrequency15/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2015 <- rbind(ViolentCrimePerCapitaPerArea2015,list("Unassigned -- Jail",0,0))

ViolentCrimePerCapitaPerArea2014 <- Violent_Crime_in_2014 %>% 
  group_by(Community) %>%
  summarize(ViolentCrimeFrequency14=n())

ViolentCrimePerCapitaPerArea2014 <-  mutate(ViolentCrimePerCapitaPerArea2014,ViolentCrimePer1000inhabitants14=((ViolentCrimePerCapitaPerArea2014$ViolentCrimeFrequency14/population_data$tpop20)*1000))

ViolentCrimePerCapitaPerArea2014 <- rbind(ViolentCrimePerCapitaPerArea2014,list("Unassigned -- Jail",0,0))

Violent_crime_evolution <- ViolentCrimePerCapitaPerArea2021 %>% 
  left_join(ViolentCrimePerCapitaPerArea2020,by="Community") %>% 
  left_join(ViolentCrimePerCapitaPerArea2019,by="Community") %>%
  left_join(ViolentCrimePerCapitaPerArea2018,by="Community") %>%
  left_join(ViolentCrimePerCapitaPerArea2017,by="Community") %>% 
  left_join(ViolentCrimePerCapitaPerArea2016,by="Community") %>% 
  left_join(ViolentCrimePerCapitaPerArea2015,by="Community") %>% 
  left_join(ViolentCrimePerCapitaPerArea2014,by="Community")

Community_data <- Community_data %>% 
  left_join(Violent_crime_evolution,by="Community")

Violent_Crime_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(VIO_PROP_CFS=="VIOLENT") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "Overall, violent crime seems to have decreased for the 2017 to 2020 period",x="Year",y="Violent crime occurences")

Violent_Crime_Yearly_evolution_map

#______________

Property_Crime_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

Property_Crime_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31")) %>% filter(VIO_PROP_CFS=="PROPERTY")

PropertyCrimePerCapitaPerArea2021 <- Property_Crime_in_2021 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency21=n())

PropertyCrimePerCapitaPerArea2021 <-  mutate(PropertyCrimePerCapitaPerArea2021,PropertyCrimePer1000inhabitants21=((PropertyCrimePerCapitaPerArea2021$PropertyCrimeFrequency21/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2021 <- rbind(PropertyCrimePerCapitaPerArea2021,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2020 <- Property_Crime_in_2020 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency20=n())

PropertyCrimePerCapitaPerArea2020 <-  mutate(PropertyCrimePerCapitaPerArea2020,PropertyCrimePer1000inhabitants20=((PropertyCrimePerCapitaPerArea2020$PropertyCrimeFrequency20/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2020 <- rbind(PropertyCrimePerCapitaPerArea2020,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2019 <- Property_Crime_in_2019 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency19=n())

PropertyCrimePerCapitaPerArea2019 <-  mutate(PropertyCrimePerCapitaPerArea2019,PropertyCrimePer1000inhabitants19=((PropertyCrimePerCapitaPerArea2019$PropertyCrimeFrequency19/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2019 <- rbind(PropertyCrimePerCapitaPerArea2019,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2018 <- Property_Crime_in_2018 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency18=n())

PropertyCrimePerCapitaPerArea2018 <-  mutate(PropertyCrimePerCapitaPerArea2018,PropertyCrimePer1000inhabitants18=((PropertyCrimePerCapitaPerArea2018$PropertyCrimeFrequency18/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2018 <- rbind(PropertyCrimePerCapitaPerArea2018,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2017 <- Property_Crime_in_2017 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency17=n())

PropertyCrimePerCapitaPerArea2017 <-  mutate(PropertyCrimePerCapitaPerArea2017,PropertyCrimePer1000inhabitants17=((PropertyCrimePerCapitaPerArea2017$PropertyCrimeFrequency17/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2017 <- rbind(PropertyCrimePerCapitaPerArea2017,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2016 <- Property_Crime_in_2016 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency16=n())

PropertyCrimePerCapitaPerArea2016 <-  mutate(PropertyCrimePerCapitaPerArea2016,PropertyCrimePer1000inhabitants16=((PropertyCrimePerCapitaPerArea2016$PropertyCrimeFrequency16/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2016 <- rbind(PropertyCrimePerCapitaPerArea2016,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2015 <- Property_Crime_in_2015 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency15=n())

PropertyCrimePerCapitaPerArea2015 <-  mutate(PropertyCrimePerCapitaPerArea2015,PropertyCrimePer1000inhabitants15=((PropertyCrimePerCapitaPerArea2015$PropertyCrimeFrequency15/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2015 <- rbind(PropertyCrimePerCapitaPerArea2015,list("Unassigned -- Jail",0,0))

PropertyCrimePerCapitaPerArea2014 <- Property_Crime_in_2014 %>% 
  group_by(Community) %>%
  summarize(PropertyCrimeFrequency14=n())

PropertyCrimePerCapitaPerArea2014 <-  mutate(PropertyCrimePerCapitaPerArea2014,PropertyCrimePer1000inhabitants14=((PropertyCrimePerCapitaPerArea2014$PropertyCrimeFrequency14/population_data$tpop20)*1000))

PropertyCrimePerCapitaPerArea2014 <- rbind(PropertyCrimePerCapitaPerArea2014,list("Unassigned -- Jail",0,0))

Property_crime_evolution <- PropertyCrimePerCapitaPerArea2021 %>% 
  left_join(PropertyCrimePerCapitaPerArea2020,by="Community") %>% 
  left_join(PropertyCrimePerCapitaPerArea2019,by="Community") %>%
  left_join(PropertyCrimePerCapitaPerArea2018,by="Community") %>%
  left_join(PropertyCrimePerCapitaPerArea2017,by="Community") %>% 
  left_join(PropertyCrimePerCapitaPerArea2016,by="Community") %>% 
  left_join(PropertyCrimePerCapitaPerArea2015,by="Community") %>% 
  left_join(PropertyCrimePerCapitaPerArea2014,by="Community")

Community_data <- Community_data %>% 
  left_join(Property_crime_evolution,by="Community")

Property_Crime_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(VIO_PROP_CFS=="PROPERTY") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "Overall, property crime seems to have decreased for the 2017 to 2020 period",x="Year",y="Property crime occurences")

Property_Crime_Yearly_evolution_map

```
###3.4.2 Calculation of felony and misdemeanor evolution

We can make the exact same computation to calculate felony and misdemeanor evolution.

```{r echo=TRUE}

Felony_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31")) %>% filter(Category=="Felony")

Felony_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31")) %>% filter(Category=="Felony")

Felony_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31")) %>% filter(Category=="Felony")

Felony_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31")) %>% filter(Category=="Felony")

Felony_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31")) %>% filter(Category=="Felony")

Felony_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31")) %>% filter(Category=="Felony")

Felony_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31")) %>% filter(Category=="Felony")

Felony_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31")) %>% filter(Category=="Felony")

FelonyPerCapitaPerArea2021 <- Felony_in_2021 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency21=n())

FelonyPerCapitaPerArea2021 <-  mutate(FelonyPerCapitaPerArea2021,FelonyPer1000inhabitants21=((FelonyPerCapitaPerArea2021$FelonyFrequency21/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2021 <- rbind(FelonyPerCapitaPerArea2021,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2020 <- Felony_in_2020 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency20=n())

FelonyPerCapitaPerArea2020 <-  mutate(FelonyPerCapitaPerArea2020,FelonyPer1000inhabitants20=((FelonyPerCapitaPerArea2020$FelonyFrequency20/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2020 <- rbind(FelonyPerCapitaPerArea2020,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2019 <- Felony_in_2019 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency19=n())

FelonyPerCapitaPerArea2019 <-  mutate(FelonyPerCapitaPerArea2019,FelonyPer1000inhabitants19=((FelonyPerCapitaPerArea2019$FelonyFrequency19/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2019 <- rbind(FelonyPerCapitaPerArea2019,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2018 <- Felony_in_2018 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency18=n())

FelonyPerCapitaPerArea2018 <-  mutate(FelonyPerCapitaPerArea2018,FelonyPer1000inhabitants18=((FelonyPerCapitaPerArea2018$FelonyFrequency18/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2018 <- rbind(FelonyPerCapitaPerArea2018,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2017 <- Felony_in_2017 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency17=n())

FelonyPerCapitaPerArea2017 <-  mutate(FelonyPerCapitaPerArea2017,FelonyPer1000inhabitants17=((FelonyPerCapitaPerArea2017$FelonyFrequency17/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2017 <- rbind(FelonyPerCapitaPerArea2017,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2016 <- Felony_in_2016 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency16=n())

FelonyPerCapitaPerArea2016 <-  mutate(FelonyPerCapitaPerArea2016,FelonyPer1000inhabitants16=((FelonyPerCapitaPerArea2016$FelonyFrequency16/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2016 <- rbind(FelonyPerCapitaPerArea2016,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2015 <- Felony_in_2015 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency15=n())

FelonyPerCapitaPerArea2015 <-  mutate(FelonyPerCapitaPerArea2015,FelonyPer1000inhabitants15=((FelonyPerCapitaPerArea2015$FelonyFrequency15/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2015 <- rbind(FelonyPerCapitaPerArea2015,list("Unassigned -- Jail",0,0))

FelonyPerCapitaPerArea2014 <- Felony_in_2014 %>% 
  group_by(Community) %>%
  summarize(FelonyFrequency14=n())

FelonyPerCapitaPerArea2014 <-  mutate(FelonyPerCapitaPerArea2014,FelonyPer1000inhabitants14=((FelonyPerCapitaPerArea2014$FelonyFrequency14/population_data$tpop20)*1000))

FelonyPerCapitaPerArea2014 <- rbind(FelonyPerCapitaPerArea2014,list("Unassigned -- Jail",0,0))

Felony_evolution <- FelonyPerCapitaPerArea2021 %>% 
  left_join(FelonyPerCapitaPerArea2020,by="Community") %>% 
  left_join(FelonyPerCapitaPerArea2019,by="Community") %>%
  left_join(FelonyPerCapitaPerArea2018,by="Community") %>%
  left_join(FelonyPerCapitaPerArea2017,by="Community") %>% 
  left_join(FelonyPerCapitaPerArea2016,by="Community") %>% 
  left_join(FelonyPerCapitaPerArea2015,by="Community") %>% 
  left_join(FelonyPerCapitaPerArea2014,by="Community")

Community_data <- Community_data %>% 
  left_join(Felony_evolution,by="Community")

Felony_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(Category=="Felony") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "In Baltimore, Felony started to decrease as from 2017",x="Year",y="Felony occurences")

Felony_Yearly_evolution_map

#___________

Misdemeanor_in_2021 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2021-01-01") & CrimeDateTime <= as.Date("2021-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2020 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2020-01-01") & CrimeDateTime <= as.Date("2020-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2019 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2019-01-01") & CrimeDateTime <= as.Date("2019-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2018 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2018-01-01") & CrimeDateTime <= as.Date("2018-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2017 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2017-01-01") & CrimeDateTime <= as.Date("2017-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2016 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2016-01-01") & CrimeDateTime <= as.Date("2016-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2015 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2015-01-01") & CrimeDateTime <= as.Date("2015-12-31")) %>% filter(Category=="Misdemeanor")

Misdemeanor_in_2014 <- crime_data_with_areas %>%  filter(CrimeDateTime >= as.Date("2014-01-01") & CrimeDateTime <= as.Date("2014-12-31")) %>% filter(Category=="Misdemeanor")

MisdemeanorPerCapitaPerArea2021 <- Misdemeanor_in_2021 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency21=n())

MisdemeanorPerCapitaPerArea2021 <-  mutate(MisdemeanorPerCapitaPerArea2021,MisdemeanorPer1000inhabitants21=((MisdemeanorPerCapitaPerArea2021$MisdemeanorFrequency21/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2021 <- rbind(MisdemeanorPerCapitaPerArea2021,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2020 <- Misdemeanor_in_2020 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency20=n())

MisdemeanorPerCapitaPerArea2020 <-  mutate(MisdemeanorPerCapitaPerArea2020,MisdemeanorPer1000inhabitants20=((MisdemeanorPerCapitaPerArea2020$MisdemeanorFrequency20/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2020 <- rbind(MisdemeanorPerCapitaPerArea2020,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2019 <- Misdemeanor_in_2019 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency19=n())

MisdemeanorPerCapitaPerArea2019 <-  mutate(MisdemeanorPerCapitaPerArea2019,MisdemeanorPer1000inhabitants19=((MisdemeanorPerCapitaPerArea2019$MisdemeanorFrequency19/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2019 <- rbind(MisdemeanorPerCapitaPerArea2019,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2018 <- Misdemeanor_in_2018 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency18=n())

MisdemeanorPerCapitaPerArea2018 <-  mutate(MisdemeanorPerCapitaPerArea2018,MisdemeanorPer1000inhabitants18=((MisdemeanorPerCapitaPerArea2018$MisdemeanorFrequency18/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2018 <- rbind(MisdemeanorPerCapitaPerArea2018,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2017 <- Misdemeanor_in_2017 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency17=n())

MisdemeanorPerCapitaPerArea2017 <-  mutate(MisdemeanorPerCapitaPerArea2017,MisdemeanorPer1000inhabitants17=((MisdemeanorPerCapitaPerArea2017$MisdemeanorFrequency17/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2017 <- rbind(MisdemeanorPerCapitaPerArea2017,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2016 <- Misdemeanor_in_2016 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency16=n())

MisdemeanorPerCapitaPerArea2016 <-  mutate(MisdemeanorPerCapitaPerArea2016,MisdemeanorPer1000inhabitants16=((MisdemeanorPerCapitaPerArea2016$MisdemeanorFrequency16/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2016 <- rbind(MisdemeanorPerCapitaPerArea2016,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2015 <- Misdemeanor_in_2015 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency15=n())

MisdemeanorPerCapitaPerArea2015 <-  mutate(MisdemeanorPerCapitaPerArea2015,MisdemeanorPer1000inhabitants15=((MisdemeanorPerCapitaPerArea2015$MisdemeanorFrequency15/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2015 <- rbind(MisdemeanorPerCapitaPerArea2015,list("Unassigned -- Jail",0,0))

MisdemeanorPerCapitaPerArea2014 <- Misdemeanor_in_2014 %>% 
  group_by(Community) %>%
  summarize(MisdemeanorFrequency14=n())

MisdemeanorPerCapitaPerArea2014 <-  mutate(MisdemeanorPerCapitaPerArea2014,MisdemeanorPer1000inhabitants14=((MisdemeanorPerCapitaPerArea2014$MisdemeanorFrequency14/population_data$tpop20)*1000))

MisdemeanorPerCapitaPerArea2014 <- rbind(MisdemeanorPerCapitaPerArea2014,list("Unassigned -- Jail",0,0))

Misdemeanor_evolution <- MisdemeanorPerCapitaPerArea2021 %>% 
  left_join(MisdemeanorPerCapitaPerArea2020,by="Community") %>% 
  left_join(MisdemeanorPerCapitaPerArea2019,by="Community") %>%
  left_join(MisdemeanorPerCapitaPerArea2018,by="Community") %>%
  left_join(MisdemeanorPerCapitaPerArea2017,by="Community") %>% 
  left_join(MisdemeanorPerCapitaPerArea2016,by="Community") %>% 
  left_join(MisdemeanorPerCapitaPerArea2015,by="Community") %>% 
  left_join(MisdemeanorPerCapitaPerArea2014,by="Community")

Community_data <- Community_data %>% 
  left_join(Misdemeanor_evolution,by="Community")

Misdemeanor_Yearly_evolution_map <- crime_data_with_areas %>%
  filter(Category=="Misdemeanor") %>% 
  count(year=floor_date(CrimeDateTime,"year")) %>% 
  ggplot(aes(year,n))+geom_line()+
  scale_x_date(limits = c(as.Date("2014-01-01"), as.Date("2020-12-31"))) +
  labs(title = "In Baltimore, Misdemeanor started to decrease as from 2017",x="Year",y="Misdemeanor occurences")

Misdemeanor_Yearly_evolution_map
```
### 3.5 Comparison of crimes and wealth

We want to investigate whether or not wealthier areas are more or less impacted by crime. To do so, we once more compute a simple linear regression. We again see that the $R^2$ is quite poor.

```{r echo=FALSE, results = 'markup'}

Crime_VS_Poverty <- CrimeStatsPerArea %>% 
  left_join(poverty_data,by=c("Community"="CSA2010"))

regression3 <- lm(Crime_VS_Poverty$CrimePer1000inhabitants~Crime_VS_Poverty$hhpov19)

stargazer(regression3,
          title = "CrimePer1000Inhabitants vs Poverty",
          type = "html")

ggplot(data=Crime_VS_Poverty,mapping= aes(x=hhpov19,y=CrimePer1000inhabitants)) + 
  labs(title = "Crime per Capita VS poverty rate", x="Poverty rate",y="Crime per Capita")+
  geom_point(shape=1) + 
  geom_smooth(method = lm,color="blue",size=0.3)

```